\subsection{Create a new intersection curve object.}
\funclabel{newIntcurve}
\begin{minipg1}
Create and initialize a SISLIntcurve-instance. Note that the arrays
{\fov guidepar1} and {\fov guidepar2} will be freed by freeIntcurve. In most cases the SISLIntcurve objects will be generated internally in the SISL intersection routines.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>SISLIntcurve *newIntcurve(\begin{minipg3}
        {\fov numgdpt}, {\fov numpar1}, {\fov numpar2}, {\fov guidepar1},\\ {\fov guidepar2}, type)
                \end{minipg3}\\[0.3ex]
                \>\>    int    \>       {\fov numgdpt};\\
                \>\>    int    \>       {\fov numpar1};\\
                \>\>    int    \>       {\fov numpar2};\\
                \>\>    double \>       {\fov guidepar1}[\,];\\
                \>\>    double \>       {\fov guidepar2}[\,];\\
                \>\>    int    \>       {\fov type};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov numgdpt}  \> - \> \begin{minipg2}
                                Number of guide points that describe the curve.
                                \end{minipg2}\\
        \>\>    {\fov numpar1} \> - \> \begin{minipg2}
                                Number of parameter directions of first object
                                involved in the intersection.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numpar2}  \> - \> \begin{minipg2}
                                Number of parameter directions of second object
                                involved in the intersection.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov guidepar1}\> - \> \begin{minipg2}
                                Parameter values of the guide points in the parameter
                                area of the first object.
                                NB! The epar1 pointer is set to point to this
                                array. The values are not copied.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov guidepar2}\> - \> \begin{minipg2}
                                Parameter values of the guide points in the parameter
                                area of the second object.
                                NB! The epar2 pointer is set to point to this
                                array. The values are not copied.
                                \end{minipg2}\\[0.3ex].
        \>\>    {\fov type} \> - \> \begin{minipg2}
                                Kind of curve, see type SISLIntcurve on
                                page \pageref{SISLIntcurve}
                                \end{minipg2}\\
\\
        \>Output Arguments:\\
        \>\>    {\fov newIntcurve} \> \> \begin{minipg2}
                                 Pointer to new SISLIntcurve. If it is impossible
                                 to allocate space for the SISLIntcurve, newIntcurve
                                 returns NULL.
                                \end{minipg2}\\
\newpagetabs
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLIntcurve    \>      *{\fov intcurve = NULL};\\
                \>\>    int    \>       {\fov numgdpt} = 2;\\
                \>\>    int    \>       {\fov numpar1} = 2;\\
                \>\>    int    \>       {\fov numpar2} = 2;\\
                \>\>    double \>       {\fov guidepar1}[4];\\
                \>\>    double \>       {\fov guidepar2}[4];\\
                \>\>    int    \>       {\fov type} = 4;\\
                \>\>    \ldots \\
        \>\>{\fov intcurve} = newIntcurve(\begin{minipg4}
                {\fov numgdpt}, {\fov numpar1}, {\fov numpar2}, {\fov guidepar1},\\ {\fov guidepar2}, type);
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \} \\
\end{tabbing}
