\subsection{Calculate the area between a 2D curve and a 2D point.}
\funclabel{s1241}
\begin{minipg1}
To calculate the area between a 2D curve and a 2D point.
               When the curve is rotating counter-clockwise around the
               point, the area contribution is positive.
               When the curve is rotating clockwise around the point,
               the area contribution is negative.
               If the curve is closed or periodic, the area calculated
               is independent of where the point is situated.
               The area is calculated exactly for B-spline curves, for
               NURBS the result is an approximation.
               This routine will only perform if the order of the curve is
               less than 7 (can easily be extended).
\end{minipg1} \\ \\
SYNOPSIS\\
        \> void s1241(\begin{minipg3}
            {\fov pcurve},  {\fov point},  {\fov dim},  {\fov epsge},  {\fov area},  {\fov stat})
                \end{minipg3}\\
                \>\>    SISLCurve    \>  *{\fov pcurve};\\
                \>\>    double    \>  {\fov point}[\,];\\
                \>\>    int    \>  {\fov dim};\\
                \>\>    double    \>  {\fov epsge};\\
                \>\>    double    \>  *{\fov area};\\
                \>\>    int    \>  *{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
        \>\>    {\fov pcurve}\> - \>  \begin{minipg2}
                     The 2D curve.
                               \end{minipg2}\\
        \>\>    {\fov point}\> - \>  \begin{minipg2}
                     The reference point.
                               \end{minipg2}\\
        \>\>    {\fov dim}\> - \>  \begin{minipg2}
                     Dimension of geometry (must be 2).
                               \end{minipg2}\\
        \>\>    {\fov epsge}\> - \>  \begin{minipg2}
                     Absolute geometrical tolerance.
                               \end{minipg2}\\
\\
	\>Output Arguments:\\
        \>\>    {\fov area}\> - \>  \begin{minipg2}
                     Calculated area.
                               \end{minipg2}\\
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : Warning.\\
                \>\>\>\>\>              $= 0$   : Ok.\\
                \>\>\>\>\>              $< 0$   : Error.\\
\\
EXAMPLE OF USE\\
		\>      \{ \\

                \>\>    SISLCurve    \>  *{\fov pcurve};\\
                \>\>    double    \>  {\fov point}[\,];\\
                \>\>    int    \>  {\fov dim};\\
                \>\>    double    \>  {\fov epsge};\\
                \>\>    double    \>  *{\fov area};\\
                \>\>    int    \>  *{\fov stat};\\                \>\>    \ldots \\
        \>\>s1241(\begin{minipg4}
            {\fov pcurve},  {\fov point},  {\fov dim},  {\fov epsge},  {\fov area},  {\fov stat});
                \end{minipg4}\\
                \>\>    \ldots \\
		\>      \}
\end{tabbing}
