\subsection{Approximate a circular arc with a curve.}
\funclabel{s1303}
\begin{minipg1}
  To create a curve approximating a circular arc around
  the axis defined by the centre point, an axis vector,
  a start point and a rotational angle.
  The maximal deviation between the true circular arc and the
  approximation to the arc is controlled by the geometric
  tolerance (epsge).
  The output will be represented as a B-spline curve.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1303(\begin{minipg3}
                {\fov startpt}, {\fov epsge}, {\fov angle}, {\fov centrept}, {\fov axis}, {\fov dim},
                {\fov curve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    double  \>      {\fov startpt}[\,];\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    double  \>      {\fov angle};\\
                \>\>    double  \>      {\fov centrept}[\,];\\
                \>\>    double  \>      {\fov axis}[\,];\\
                \>\>    int     \>      {\fov dim};\\
                \>\>    SISLCurve       \>      **{\fov curve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov startpt}  \> - \> Start point of the circular arc\\
        \>\>    {\fov epsge}    \> - \> \begin{minipg2}
                                Maximal deviation allowed between the true
                                circle and the circle approximation.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov angle}    \> - \> \begin{minipg2}
                                The rotational angle. Counterclockwise around
                                axis. If the rotational angle
                                is outside $<-2\pi,+2\pi>$
                                then a closed curve is produced.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov centrept}\> - \>  Point on the axis of the circle.\\
        \>\>    {\fov axis}     \> - \> \begin{minipg2}
                                Normal vector to plane in which the circle lies.
                                Used if dim = 3.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov dim}      \> - \> \begin{minipg2}
                                The dimension of the space in which the
                                circular arc lies (2 or 3).
                                \end{minipg2}\\[0.3ex]
\\
\newpagetabs
        \>Output Arguments:\\
        \>\>    {\fov curve}    \> - \> Pointer to the B-spline curve.\\
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    double  \>      {\fov startpt}[3];\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    double  \>      {\fov angle};\\
                \>\>    double  \>      {\fov centrept}[3];\\
                \>\>    double  \>      {\fov axis}[3];\\
                \>\>    int     \>      {\fov dim} = 3;\\
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1303(\begin{minipg4}
                        {\fov startpt}, {\fov epsge}, {\fov angle}, {\fov centrept},
                        {\fov axis}, {\fov dim}, \&{\fov curve}, \&{\fov stat});
                \end{minipg4}\\
                \>\>    \ldots \\
                \>      \} \\
\end{tabbing}
