\subsection{Lofted surface.}
\funclabel{s1333}
\begin{minipg1}
To create a spline lofted surface from a set of input curves.
\end{minipg1} \\ \\
SYNOPSIS\\
	\>void s1333(\begin{minipg3}
			{\fov numcurve}, {\fov curves}, {\fov typecur}, {\fov startpar}, {\fov open}, {\fov order2},
			{\fov flag}, {\fov surf}, {\fov parval}, {\fov stat})
		\end{minipg3}\\[0.3ex]
		\>\>	int	\> 	{\fov numcurve};\\
		\>\>	SISLCurve	\>	*{\fov curves}[\,];\\
		\>\>	int	\>	{\fov typecur}[\,];\\
		\>\>	double	\>	{\fov startpar};\\
		\>\>	int 	\>	{\fov open};\\
		\>\>	int 	\>	{\fov order2};\\
		\>\>	int	\>	{\fov flag};\\
		\>\>	SISLSurf	\>	**{\fov surf};\\
		\>\>	double 	\>	**{\fov parval};\\
		\>\>	int 	\>	*{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
	\>\>	{\fov numcurve}\> - \>	\begin{minipg2}
				Number of curves in the curve-set.
				\end{minipg2}\\
	\>\>	{\fov curves}\> - \>	\begin{minipg2}
				Array (length numcurve) of pointers to the curves in the 
				curve-set.
				\end{minipg2}\\[0.8ex]
	\>\>	{\fov typecur}\> - \>	\begin{minipg2}
				Array (length numcurve) containing the types of the curves	
				in the curve-set.
				\end{minipg2}\\[0.8ex]
		\>\>\>\>\>	 1 : \>	Ordinary curve.\\
		\>\>\>\>\>	 3 : \>	Tangent to next curve.\\
		\>\>\>\>\>	 4 : \>	Tangent to prior curve.\\
		\>\>\>\>\>	13 : \>	\begin{minipg5}
					SISLCurve giving start of the tangent to next curve.
					\end{minipg5}\\[0.8ex]
		\>\>\>\>\>	14 : \>	\begin{minipg5}
					SISLCurve giving end of the tangent to prior curve.
					\end{minipg5}\\[0.8ex]
	\>\>	{\fov startpar}\> - \>	\begin{minipg2}
				Start parameter of the parameter interval in the spline lofting direction.	
				\end{minipg2} \\[0.3ex]
	\>\>	{\fov open}\> - \>	\begin{minipg2}
				Flag specifying if the resulting surface from the lofting should be closed 
						or open.
				\end{minipg2} \\[0.8ex]
		\>\>\>\>\>	$=0$ : \>	The surface should be closed.\\
		\>\>\>\>\>	$=1$ : \>	The surface should be open.\\
{\fov 	}\>\>	order2	\> - \> \begin{minipg2}
				Maximal order of the B-spline basis in the lofting 	
				direction.
				\end{minipg2}\\[0.8ex]
	\>\>	{\fov flag}\> - \>	\begin{minipg2}
				Flag specifying if the length of the
				tangents in the derivative curves 
				should be adjusted or not.
				\end{minipg2}\\[0.3ex]
		\>\>\>\>\>	$=0$ : \>	Do not adjust tangent-lengths.\\
		\>\>\>\>\>	$=1$ : \>	Adjust tangent-lengths\\
\\
	\>Output Arguments:\\
	\>\>	{\fov surf}\> - \>	\begin{minipg2}
				Pointer to the produced surface .
				\end{minipg2}\\
	\>\>	{\fov parval}\> - \>	\begin{minipg2}
			The input curves are constant parameter lines in the parameter
			plane of the produced surface.
				\end{minipg2}\\[0.3ex]
		\>\>\>\>\>	[i]: \>	\begin{minipg5}
					contains the (constant) parameter value of input curve no. i.
					\end{minipg5}\\[0.3ex]
	\>\>	{\fov stat}\> - \>		Status messages\\
		\>\>\>\>\>		$> 0$	: warning\\
		\>\>\>\>\>		$= 0$	: ok\\
		\>\>\>\>\>		$< 0$	: error\\		
\\
EXAMPLE OF USE\\
		\>	\{ \\
		\>\>	int	\> 	{\fov numcurve = 4};\\
		\>\>	SISLCurve	\>	*{\fov curves[4]};\\
		\>\>	int	\>	{\fov typecur[4]};\\
		\>\>	double	\>	{\fov startpar};\\
		\>\>	int 	\>	{\fov open};\\
		\>\>	int 	\>	{\fov order2};\\
		\>\>	int	\>	{\fov flag};\\
		\>\>	SISLSurf	\>	*{\fov surf};\\
		\>\>	double 	\>	*{\fov parval};\\
		\>\>	int 	\>	{\fov stat};\\
		\>\>	\ldots \\
	\>\>s1333(\begin{minipg4}
		{\fov numcurve}, {\fov curves}, {\fov typecur}, {\fov startpar}, {\fov open}, {\fov order2}, {\fov flag}, \&{\fov surf},	
		\&{\fov parval}, \&{\fov stat});
			\end{minipg4}\\
		\>\>	\ldots\\
		\>	\}
\end{tabbing}
