\subsection{Compute a curve interpolating a set of points,
parameter\-ization as input.}
\funclabel{s1357}
\begin{minipg1}
Compute a curve interpolating a set of points.  The points
can be assigned a tangent (derivative).  The curve can be open, closed
or periodic. If end-conditions are conflicting, the condition closed
curve rules out other end conditions. The parameterization is given by
the array {\fov epar}.
The output will be represented as a B-spline curve.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1357(\begin{minipg3}
        {\fov epoint}, {\fov inbpnt}, {\fov idim}, {\fov ntype}, {\fov epar}, {\fov icnsta}, {\fov icnend}, {\fov iopen}, {\fov ik}, {\fov astpar},
        {\fov cendpar}, {\fov rc}, {\fov gpar}, {\fov jnbpar}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    double \>  {\fov epoint}[\,];\\
        \>\>    int    \>  {\fov inbpnt};\\
        \>\>    int    \>  {\fov idim};\\
        \>\>    int    \>  {\fov ntype}[\,];\\
        \>\>    double \>  {\fov epar}[\,];\\
        \>\>    int    \>  {\fov icnsta};\\
        \>\>    int    \>  {\fov icnend};\\
        \>\>    int    \>  {\fov iopen};\\
        \>\>    int    \>  {\fov ik};\\
        \>\>    double \>  {\fov astpar};\\
        \>\>    double \>  *{\fov cendpar};\\
        \>\>    SISLCurve \> **{\fov rc};\\
        \>\>    double \>  **{\fov gpar};\\
        \>\>    int    \>  *{\fov jnbpar};\\
        \>\>    int    \>  *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov epoint}\> - \>
        \begin{minipg2}
          Array (length $idim\times inbpnt$) containing the
          points/\-derivatives to be interpolated.
        \end{minipg2}\\
        \>\>    {\fov inbpnt}\> - \>
        \begin{minipg2}
          No. of points/\-derivatives in the {\fov epoint} array.
        \end{minipg2}\\
        \>\>    {\fov idim}\> - \>
        The dimension of the space in which the points lie.\\
        \>\>    {\fov ntype}\> - \> \begin{minipg2}
                  Array (length {\fov inbpnt}) containing type indicator for
                  points/\-derivatives/\-second-derivatives:
                \end{minipg2}\\
                \>\>\>\> $=1$\>: Ordinary point.\\
                \>\>\>\> $=2$\>:
                \begin{minipg5}
                  Knuckle point.  (Is treated as an ordinary point.)
                \end{minipg5}\\
                \>\>\>\> $=3$\>: Derivative to next point.\\
                \>\>\>\> $=4$\>: Derivative to prior point.\\
                \>\>\>\> ($=5$\>: Second-derivative to next point.)\\
                \>\>\>\> ($=6$\>: Second derivative to prior point.)\\
                \>\>\>\> $=13$\>: Point of tangent to next point.\\
                \>\>\>\> $=14$\>: Point of tangent to prior  point.\\
        \>\>    {\fov epar}\> - \>
        \begin{minipg2}
          Array containing the wanted parameterization. Only parameter
          values corresponding to position points are given.
          For closed curves, one additional parameter value
          must be specified. The last entry contains
          the parametrization of the repeated start point.
          (if the end point is equal to the start point of
          the interpolation the length of the array should
          be equal to inpt1 also in the closed case).
        \end{minipg2}\\
        \>\>    {\fov icnsta}\> - \>
                Additional condition at the start of the curve:\\
                  \>\>\>\> $=0$\>: No additional condition.\\
                  \>\>\>\> $=1$\>: Zero curvature at start.\\
        \>\>    {\fov icnend}\> - \>
                Additional condition at the end of the curve:\\
                  \>\>\>\> $=0$\>: No additional condition.\\
                  \>\>\>\> $=1$\>: Zero curvature at end.\\
        \>\>    {\fov iopen}\> - \>
                Flag telling if the curve should be open or closed:\\
                  \>\>\>\> $=1$\>: The curve should be open.\\
                  \>\>\>\> $=0$\>: The curve should be closed.\\
                  \>\>\>\> $=-1$\>: The curve should be closed and periodic.\\
        \>\>    {\fov ik}\> - \> The order of the spline curve to be produced.\\
        \>\>    {\fov astpar}\> - \>
        \begin{minipg2}
          Parameter value to be used at the start of the curve.
        \end{minipg2}\\
\\
        \>Output Arguments:\\
        \>\>    {\fov cendpar}\> - \>
        \begin{minipg2}
          Parameter value used at the end of the curve.
        \end{minipg2}\\
        \>\>    {\fov rc}\> - \> Pointer to the output B-spline curve.\\
        \>\>    {\fov gpar}\> - \>
        \begin{minipg2}
          Pointer to the parameter values of the points in the
          curve. Represented only once, although derivatives and
          second-derivatives will have the same parameter value as the
          points.
        \end{minipg2}\\
        \>\>    {\fov jnbpar}\> - \>  No, of unique parameter values.\\
        \>\>    {\fov jstat}\> - \> Status message\\
                \>\>\>\>\> $< 0$ : Error.\\
                \>\>\>\>\> $= 0$ : Ok.\\
                \>\>\>\>\> $> 0$ : Warning.\\
\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    double \>  {\fov epoint}[30];\\
        \>\>    int    \>  {\fov inbpnt} = 10;\\
        \>\>    int    \>  {\fov idim} = 3;\\
        \>\>    int    \>  {\fov ntype}[10];\\
        \>\>    double \>  {\fov epar}[10];\\
        \>\>    int    \>  {\fov icnsta} = 0;\\
        \>\>    int    \>  {\fov icnend} = 0;\\
        \>\>    int    \>  {\fov iopen} = 0;\\
        \>\>    int    \>  {\fov ik} = 4;\\
        \>\>    double \>  {\fov astpar} = 0.0;\\
        \>\>    double \>  {\fov cendpar};\\
        \>\>    SISLCurve \> *{\fov rc};\\
        \>\>    double \>  *{\fov gpar};\\
        \>\>    int    \>  {\fov jnbpar};\\
        \>\>    int    \>  {\fov jstat};\\
        \>\>    \ldots \\
        \>\>s1357(\begin{minipg4}
          {\fov epoint}, {\fov inbpnt}, {\fov idim}, {\fov ntype}, {\fov epar}, {\fov icnsta}, {\fov icnend}, {\fov iopen}, {\fov ik}, {\fov astpar},
          \&{\fov cendpar}, \&{\fov rc}, \&{\fov gpar}, \&{\fov jnbpar}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
