\subsection{Compute a surface approximating the offset of a surface.}
\funclabel{s1365}
\begin{minipg1}
  Create a surface approximating the offset of a surface.
  The output is represented as a B-spline surface.\\
  With an offset of zero, this routine can be used to approximate any
  NURBS (rational) surface with a B-spline (non-rational) surface.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1365(\begin{minipg3}
          {\fov ps}, {\fov aoffset}, {\fov aepsge}, {\fov amax}, {\fov idim}, {\fov rs}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    SISLSurf \> *{\fov ps};\\
        \>\>    double   \> {\fov aoffset};\\
        \>\>    double   \> {\fov aepsge};\\
        \>\>    double   \> {\fov amax};\\
        \>\>    int      \> {\fov idim};\\
        \>\>    SISLSurf \> **{\fov rs};\\
        \>\>    int      \> *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov ps} \> - \> The input surface.\\
        \>\>    {\fov aoffset} \> - \>
        \begin{minipg2}
          The offset distance.
          If $idim=2$ a positive signe on this value put the
          offset on the side of the positive normal vector,
          and a negative sign puts the offset on the sign
          of the negative normal vector.
          If $idim=3$ the offset is determined by the cross
          product of the tangent vector and the anorm vector.
          The offset distance is multiplied by this vector.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov aepsge} \> - \>
        \begin{minipg2}
          Maximal deviation allowed between true offset surface
          and the approximated offset surface.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov amax} \> - \>
        \begin{minipg2}
          Maximal stepping length. Is negleceted if $amax\leq aepsge$.
          If $amax=0$ then a maximal step length of the longest box side
          is used.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov idim} \> - \> The dimension of the space (2 or 3).
\\
        \>Output Arguments:\\
        \>\>    {\fov rs} \> - \>
        \begin{minipg2}
          The approximated offset represented as
          a \mbox{B-spline} surface.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov jstat} \> - \> Status message\\
                \>\>\>\>\> $< 0$ : Error.\\
                \>\>\>\>\> $= 0$ : Ok.\\
                \>\>\>\>\> $> 0$ : Warning.\\
\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    SISLSurf \> *{\fov ps};\\
        \>\>    double   \> {\fov aoffset};\\
        \>\>    double   \> {\fov aepsge};\\
        \>\>    double   \> {\fov amax};\\
        \>\>    int      \> {\fov idim};\\
        \>\>    SISLSurf \> *{\fov rs};\\
        \>\>    int      \> {\fov jstat};\\
        \>\>    \ldots \\
        \>\>s1365(\begin{minipg4}
          {\fov ps}, {\fov aoffset}, {\fov aepsge}, {\fov amax}, {\fov idim}, \&{\fov rs}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
