\subsection{Intersection between a curve and a torus.}
\funclabel{s1375}
\begin{minipg1}
  Find all the intersections between a curve and a torus.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1375(\begin{minipg3}
        {\fov curve}, {\fov centre}, {\fov normal}, {\fov centdist}, {\fov rad}, {\fov dim}, {\fov epsco}, {\fov epsge},\\ {\fov numintpt}, {\fov intpar},
                        {\fov numintcu}, {\fov intcurve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov centre[\,]};\\
                \>\>    double  \>      {\fov normal}[\,];\\
                \>\>    double  \>      {\fov centdist};\\
                \>\>    double  \>      {\fov rad};\\
                \>\>    int             \>      {\fov dim};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov numintpt};\\
                \>\>    double  \>      **{\fov intpar};\\
                \>\>    int     \>      *{\fov numintcu};\\
                \>\>    SISLIntcurve \> ***{\fov intcurve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve}    \> - \> Pointer to the curve.\\
        \>\>    {\fov centre}   \> - \> \begin{minipg2}
                                The centre of the torus (lying in the symmetry plane)
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov normal}   \> - \> Normal of symmetry plane.\\
        \>\>    {\fov centdist}\> - \>  \begin{minipg2}
                                Distance from the centre of the cone to the centre circle of the torus.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov rad}      \> - \> The radius of the torus surface.\\
        \>\>    {\fov dim}      \> - \> \begin{minipg2}
                                Dimension of the space in which the
                                torus and the curve
                                lie, dim should be equal to  three.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov epsco}    \> - \> Computational resolution (not used).\\
        \>\>    {\fov epsge}    \> - \> Geometry resolution.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov numintpt}\> - \>  Number of single intersection points.\\
        \>\>    {\fov intpar}   \> - \> \begin{minipg2}
                        Array containing the parameter values of the
                        single intersection points in the parameter
                        interval of the curve. The points lie in sequence.
                        Intersection curves are stored in intcurve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numintcu}\> - \>Number of intersection curves.\\
        \>\>    {\fov intcurve}\> - \>  \begin{minipg2}
                        Array of pointers to the SISLIntcurve objects
                        containing descriptions of the intersection
                        curves. The curves are only described by start
                        points and end points in
                        the parameter interval of the curve. The curve
                        pointers point to nothing.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov centre}[3];\\
                \>\>    double  \>      {\fov normal}[3];\\
                \>\>    double  \>      {\fov centdist};\\
                \>\>    double  \>      {\fov rad};\\
                \>\>    int     \>      {\fov dim} = 3;\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      {\fov numintpt};\\
                \>\>    double  \>      *{\fov intpar};\\
                \>\>    int     \>      {\fov numintcu};\\
                \>\>    SISLIntcurve \> **{\fov intcurve};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    {\fov \ldots} \\
        \>\>s1375(\begin{minipg4}
        {\fov curve}, {\fov centre}, {\fov normal}, {\fov centdist}, {\fov rad}, {\fov dim}, {\fov epsco}, {\fov epsge},\\ \&{\fov numintpt},
                \&{\fov intpar}, \&{\fov numintcu}, \&{\fov intcurve}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
