\subsection{Compute a first derivative continuous blending surface set,
over a 3-, 4-, 5- or 6-sided region in space, from a set of B-spline
input curves.}
\funclabel{s1391}
\begin{minipg1}
  To create a first derivative continuous blending surface set over a
  3-, 4-, 5- and 6-sided region in space. The boundary of the
  region are B-spline (i.e.\ NOT rational) curves and the cross boundary
  derivatives  are given as B-spline (i.e.\ NOT rational) curves.
  This function automatically
  preprocesses the input cross tangent curves in order to
  make them suitable for the blending. Thus, the cross tangent
  curves should be taken as the cross tangents of the
  surrounding surface. It is not necessary and not advisable
  to match tangents etc. in the corners.
  The output is represented as a set of B-spline surfaces.
\end{minipg1}\\ \\
SYNOPSIS\\
        \>void s1391(\begin{minipg3}
          {\fov pc}, {\fov ws}, {\fov icurv}, {\fov nder}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    SISLCurve \> **{\fov pc};\\
        \>\>    SISLSurf  \> ***{\fov ws};\\
        \>\>    int       \>  {\fov icurv};\\
        \>\>    int       \>  {\fov nder}[\,];\\
        \>\>    int       \>  *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov pc} \> - \>
        \begin{minipg2}
          Pointers to boundary B-spline curves. All curves must
          have same parameter direction around the patch,
          either clockwise or counterclockwise.
          $pc1[i], i=0,\dots nder[0]-1$ are pointers to position
          and cross-derivatives along first edge.
          $pc1[i], i=nder[0],\dots nder[1]-1$ are pointers
          to position and cross-derivatives along second edge.\\
          \hspace*{4em}$\vdots$\\
          \[
            pc1[i], i=nder[0]+\dots+nder[icurv-2],\dots, nder[icurv-1]-1
          \]
          are pointers to position and cross-derivatives along fourth edge.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov icurv} \> - \> Number of boundary curves (3, 5, 4 or 6).\\
        \>\>    {\fov nder} \> - \>
        \begin{minipg2}
          {\fov nder[i]} gives number of curves on edge number
          $i+1$. These numbers has to be equal to 2.
          The vector is of length {\fov icurv}.
        \end{minipg2}\\[0.8ex]
\\
\newpagetabs
        \>Output Arguments:\\
        \>\>    {\fov ws} \> - \>
        \begin{minipg2}
          These are pointers to the blending B-spline surfaces. The vector is of
          length {\fov icurv}.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov jstat} \> - \> Status message\\
                \>\>\>\>\> $< 0$ : Error.\\
                \>\>\>\>\> $= 0$ : Ok.\\
                \>\>\>\>\> $> 0$ : Warning.\\
\\
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    SISLCurve \> **{\fov pc};\\
        \>\>    SISLSurf  \> **{\fov ws} = NULL;\\
        \>\>    int       \> {\fov icurv} = 5;\\
        \>\>    int       \> {\fov nder}[5];\\
        \>\>    int       \> {\fov jstat} = 0;\\
        \>\>    \ldots \\
        \>\>s1391(\begin{minipg4}
          {\fov pc}, \&{\fov ws}, {\fov icurv}, {\fov nder}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
