\subsection{Compute a surface, representing a Gordon patch, from a set
of B-spline input curves.}
\funclabel{s1401}
\begin{minipg1}
  Compute a Gordon patch, given position and cross tangent conditions as
  B-spline (i.e.\ NOT rational) curves at the boundary of a squared
  region and the twist vector in the corners.
  The output is represented as a B-spline surface.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1401(\begin{minipg3}
          {\fov vcurve}, {\fov etwist}, {\fov rsurf}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    double    \> {\fov etwist}[\,];\\
        \>\>    SISLCurve \> *{\fov vcurve}[\,];\\
        \>\>    int       \> *{\fov jstat};\\
        \>\>    SISLSurf  \> **{\fov rsurf};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov vcurve} \> - \>
        \begin{minipg2}
          Position and cross-tangent B-spline curves around the square
          region. For each edge of the region position and cross-tangent
          curves are given. The dimension of the array is 8.
        \end{minipg2}\\[0.8ex]
        \>\>\>\>\begin{minipg2}
                  The orientation is as follows:\\
                  \begin{center}
                    \begin{picture}(180,110)(0,0)
                      \put(50,15){\framebox(80,80)}
                      \put(40,55){\vector(0,1){20}}
                      \put(140,55){\vector(0,1){20}}
                      \put(90,5){\vector(1,0){20}}
                      \put(90,105){\vector(1,0){20}}
                      \put(40,45){\makebox(0,0){4}}
                      \put(140,45){\makebox(0,0){2}}
                      \put(80,5){\makebox(0,0){1}}
                      \put(80,105){\makebox(0,0){3}}

                      \put(60,20){\vector(1,0){40}}
                      \put(85,28){\makebox(0,0){$(i)$}}
                      \put(55,25){\vector(0,1){40}}
                      \put(65,50){\makebox(0,0){$(ii)$}}
                    \end{picture}\\
                    $(i) \; \; \;$ first parameter direction of the surface.\\
                    $(ii)$   second parameter direction of the surface.\\
                  \end{center}
                \end{minipg2}\\ \\
        \>\>    {\fov etwist} \> - \>
        \begin{minipg2}
          Twist-vectors of the corners of the vertex region. The first
          element of the array is the twist in the corner before the
          first edge, etc. The dimension of the array is 4 times the
          spatial dimension of the input curves (currently only 3D).
        \end{minipg2}\\[0.8ex]
\newpagetabs
        \>Output Arguments:\\
        \>\>    {\fov rsurf} \> - \> Gordons-patch represented as a
                                     B-spline surface.\\
        \>\>    {\fov jstat} \> - \> Status message\\
                \>\>\>\>\> $< 0$ : Error.\\
                \>\>\>\>\> $= 0$ : Ok.\\
                \>\>\>\>\> $> 0$ : Warning.\\
\\
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    int       \> {\fov idim} = 3;\\
        \>\>    double    \> {\fov etwist}[4*{\fov idim}];\\
        \>\>    SISLCurve \> *{\fov vcurve}[8];\\
        \>\>    int       \> {\fov jstat} = 0;\\
        \>\>    SISLSurf  \> *{\fov rsurf} = NULL;\\
        \>\>    \ldots \\
        \>\>s1401(\begin{minipg4}
          {\fov vcurve}, {\fov etwist}, \&{\fov rsurf}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
