\subsection{Compute area, weight point and moment of inertia of a B-spline patch.}
\funclabel{s1442}
\begin{minipg1}
Compute the area and the weight point of a surface by using recursive 
subdivision. The rotational momentum relative to  a given axis is also 
calculated. The difference between the area computed and the real area of the 
surface is less than (epssurf/area computed).
\end{minipg1} \\ \\
SYNOPSIS\\
	\>void s1442(\begin{minipg3}
			{\fov surf}, {\fov point}, {\fov dir}, {\fov dim}, {\fov epssurf}, {\fov epsge}, {\fov weight}, {\fov area}, 	
			{\fov moment}, {\fov stat})
		\end{minipg3}\\[0.3ex]

		\>\>	SISLSurf	\> 	*{\fov surf};\\
		\>\>	double	\>	{\fov point}[\,];\\
		\>\>	double	\>	{\fov dir}[\,];\\
		\>\>	int	\>	{\fov dim};\\
		\>\>	double	\>	{\fov epssurf};\\
		\>\>	double	\>	{\fov epsge};\\
		\>\>	double	\>	{\fov weight}[\,];\\
		\>\>	double 	\>	*{\fov area};\\
		\>\>	double 	\>	*{\fov moment};\\
		\>\>	int 	\>	*{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
	\>\>	{\fov surf}\> - \>	\begin{minipg2}
				Pointer to the surface.
				\end{minipg2}\\
	\>\>	{\fov point}\> - \>	\begin{minipg2}
				(Reference) point on the rotational axis.
				\end{minipg2}\\
	\>\>	{\fov dir}\> - \>	\begin{minipg2}
				Direction of the rotational axis.	
				\end{minipg2}\\
	\>\>	{\fov dim}\> - \>	\begin{minipg2}
				Dimension of the space in which point and dir lie.
				\end{minipg2} \\
	\>\>	{\fov epssurf}\> - \> 	\begin{minipg2}
				Relative resolution used on surfaces.
				\end{minipg2}\\
	\>\>	{\fov epsge}\> - \>	\begin{minipg2}
				Geometry resolution.
				\end{minipg2}\\
\\
	\>Output Arguments:\\
	\>\>	{\fov weight}\> - \>	\begin{minipg2}
				Area weight point.
				\end{minipg2}\\
	\>\>	{\fov area}\> - \>	\begin{minipg2}
				The area calculated.
				\end{minipg2}\\
	\>\>	{\fov moment}\> - \>	\begin{minipg2}
				Rotational weight moment.
				\end{minipg2}\\
	\>\>	{\fov stat}	\> - \>	Status messages\\
		\>\>\>\>\>		$> 0$	: warning\\
		\>\>\>\>\>		$= 0$	: ok\\
		\>\>\>\>\>		$< 0$	: error\\
\\
EXAMPLE OF USE\\
		\>	\{ \\
		\>\>	SISLSurf	\> 	*surf;\\
		\>\>	double	\>	{\fov point}[3];\\
		\>\>	double	\>	{\fov dir}[3];\\
		\>\>	int	\>	{\fov dim} = 3;\\
		\>\>	double	\>	{\fov epssurf};\\
		\>\>	double	\>	{\fov epsge};\\
		\>\>	double	\>	{\fov weight}[3];\\
		\>\>	double 	\>	{\fov area};\\
		\>\>	double 	\>	{\fov moment};\\
		\>\>	int 	\>	{\fov stat};\\
		\>\>	\ldots \\
	\>\>s1442(\begin{minipg4}
		{\fov surf}, {\fov point}, {\fov dir}, {\fov dim}, {\fov epssurf}, {\fov epsge}, {\fov weight}, \&{\fov area}, 		
		\&{\fov moment}, \&{\fov stat});
			\end{minipg4}\\
		\>\>	\ldots \\
		\>	\}
\end{tabbing}
