\subsection{Intersection between a curve and an elliptic cone.}
\funclabel{s1502}
\begin{minipg1}
  Find all the intersections between a curve and an elliptic cone.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1502(\begin{minipg3}
         {\fov curve}, {\fov basept}, {\fov normdir}, {\fov ellipaxis}, {\fov alpha}, {\fov ratio}, {\fov dim}, {\fov epsco}, {\fov epsge}, {\fov numintpt}, {\fov intpar},
                        {\fov numintcu}, {\fov intcurve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov basept}[\,];\\
                \>\>    double  \>      {\fov normdir}[\,];\\
                \>\>    double  \>      {\fov ellipaxis}[\,];\\
                \>\>    double  \>      {\fov alpha};\\
                \>\>    double  \>      {\fov ratio};\\
                \>\>    int     \>      {\fov dim};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov numintpt};\\
                \>\>    double  \>      **{\fov intpar};\\
                \>\>    int     \>      *{\fov numintcu};\\
                \>\>    SISLIntcurve \> ***{\fov intcurve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve}    \> - \> Pointer to the curve.\\
        \>\>    {\fov basept}\> - \>    \begin{minipg2}
                                Base point of the cone, centre of elliptic base.
                                \end{minipg2}\\
        \>\>    {\fov normdir}\> - \>   \begin{minipg2}
                                Direction of the cone axis, normal to the elliptic base. The default is pointing from the base point to the top point of the cone.
                                \end{minipg2}\\
        \>\>    {\fov ellipaxis}\> - \> \begin{minipg2}
                                One of the axes of the ellipse (major or minor).
                                \end{minipg2}\\
        \>\>    {\fov alpha}\> - \>     \begin{minipg2}
                                The opening angle of the cone at the ellipaxis.
                                \end{minipg2}\\
        \>\>    {\fov ratio}\> - \>     \begin{minipg2}
                                The ratio of the major and minor
                                axes = ellipaxis/otheraxis.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov dim}      \> - \> \begin{minipg2}
                                Dimension of the space in which the
                                cone and the curve
                                lie, dim should be equal to three.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov epsco}    \> - \> Computational resolution (not used).\\
        \>\>    {\fov epsge}    \> - \> Geometry resolution.\\
\newpagetabs
        \>Output Arguments:\\
        \>\>    {\fov numintpt}\> - \>  Number of single intersection points.\\
        \>\>    {\fov intpar}   \> - \> \begin{minipg2}
                        Array containing the parameter values of the
                        single intersection points in the parameter
                        interval of the curve. The points lie in sequence.
                        Intersection curves are stored in intcurve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numintcu}\> - \>Number of intersection curves.\\
        \>\>    {\fov intcurve}\> - \>  \begin{minipg2}
                        Array of pointers to the SISLIntcurve object
                        containing descriptions of the intersection
                        curves. The curves are only described by start
                        points and end points in
                        the parameter interval of the curve. The curve
                        pointers point to nothing.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov basept}[3];\\
                \>\>    double  \>      {\fov normdir}[3];\\
                \>\>    double  \>      {\fov ellipaxis}[3];\\
                \>\>    double  \>      {\fov alpha};\\
                \>\>    double  \>      {\fov ratio};\\
                \>\>    int     \>      {\fov dim} = 3;\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      {\fov numintpt};\\
                \>\>    double  \>      *{\fov intpar};\\
                \>\>    int     \>      {\fov numintcu};\\
                \>\>    SISLIntcurve \> **{\fov intcurve};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1502(\begin{minipg4}
        {\fov curve}, {\fov basept}, {\fov normdir}, {\fov ellipaxis}, {\fov alpha}, {\fov ratio}, {\fov dim}, {\fov epsco}, {\fov epsge}, \&{\fov numintpt},
                \&{\fov intpar}, \&{\fov numintcu}, \&{\fov intcurve}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
