\subsection{\sloppy Compute a surface by Hermite interpolation, automatic parameter\-ization.}
\funclabel{s1529}
\begin{minipg1}
  Compute the cubic Hermite surface interpolant to the data given.
  More specifically, given positions, (u',v), (u,v'), and (u',v')
  derivatives at points of a rectangular grid,
  the routine
  computes a cubic tensor-product B-spline interpolant to
  the given data with double knots at each data (the first
  knot vector will have double knots at all interior points
  in epar1, quadruple knots at the first and last points,
  and similarly for the second knot vector).
  The output is represented as a B-spline surface.
\end{minipg1}\\ \\
SYNOPSIS\\
        \>void s1529(\begin{minipg3}
          {\fov ep}, {\fov eder10}, {\fov eder01}, {\fov eder11},
          {\fov im1}, {\fov im2}, {\fov idim}, {\fov ipar}, {\fov rsurf}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    double \>  {\fov ep}[\,];\\
        \>\>    double \>  {\fov eder10}[\,];\\
        \>\>    double \>  {\fov eder01}[\,];\\
        \>\>    double \>  {\fov eder11}[\,];\\
        \>\>    int    \>  {\fov im1};\\
        \>\>    int    \>  {\fov im2};\\
        \>\>    int    \>  {\fov idim};\\
        \>\>    int    \>  {\fov ipar};\\
        \>\>    SISLSurf \>  **{\fov rsurf};\\
        \>\>    int    \>  *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov ep}     \> - \>
        \begin{minipg2}
          Array of dimension $idim\times im1\times im2$ containing the
          positions of the nodes (using the same ordering as ecoef in
          the SISLSurf structure).
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov eder10} \> - \>
        \begin{minipg2}
          Array of dimension $idim\times im1\times im2$ containing the
          first derivative in the first parameter direction.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov eder01} \> - \>
        \begin{minipg2}
          Array of dimension $idim\times im1\times im2$ containing the
          first derivative in the second parameter direction.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov eder11} \> - \>
        \begin{minipg2}
          Array of dimension $idim\times im1\times im2$ containing the
          cross derivative (twist vector).
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov ipar}   \> - \>
          Flag showing the desired parametrization to be used:\\
          \>\>\>\>$= 1$\>:
          \begin{minipg5}
            Mean accumulated cord-length para\-meter\-ization.
          \end{minipg5}\\[0.8ex]
          \>\>\>\>$= 2$\>: Uniform parametrization.\\
        \>\>    {\fov im1}    \> - \>
        \begin{minipg2}
          The number of interpolation points in the first parameter
          direction.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov im2}    \> - \>
        \begin{minipg2}
          The number of interpolation points in the second parameter
          direction.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov idim}   \> - \> Spatial dimension.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov rsurf}  \> - \> Pointer to the B-spline surface produced.\\
        \>\>    {\fov jstat}  \> - \> Status message\\
                \>\>\>\>\> $< 0$ : Error.\\
                \>\>\>\>\> $= 0$ : Ok.\\
                \>\>\>\>\> $> 0$ : Warning.\\
\\ %\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    double \>  {\fov ep}[300];\\
        \>\>    double \>  {\fov eder10}[300];\\
        \>\>    double \>  {\fov eder01}[300];\\
        \>\>    double \>  {\fov eder11}[300];\\
        \>\>    int    \>  {\fov im1} = 10;\\
        \>\>    int    \>  {\fov im2} = 10;\\
        \>\>    int    \>  {\fov idim} = 3;\\
        \>\>    int    \>  {\fov ipar};\\
        \>\>    SISLSurf \> *{\fov rsurf} = NULL;\\
        \>\>    int    \>  {\fov jstat} = 0;\\
        \>\>    \ldots \\
        \>\>s1529(
        \begin{minipg4}
          {\fov ep}, {\fov eder10}, {\fov eder01}, {\fov eder11},
          {\fov im1}, {\fov im2}, {\fov idim}, {\fov ipar}, \&{\fov rsurf}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
