\subsection{Create a lofted surface
               from a set of B-spline input curves and parametrization.}
\funclabel{s1539}
\begin{minipg1}
To create a spline lofted surface
               from a set of input curves. The parametrization
               of the position curves is given in epar.
\end{minipg1} \\ \\
SYNOPSIS\\
        \> void s1539(\begin{minipg3}
            {\fov inbcrv}, {\fov vpcurv}, {\fov nctyp}, {\fov epar}, {\fov astpar}, {\fov iopen}, {\fov iord2},
            {\fov iflag}, {\fov rsurf}, {\fov gpar}, {\fov jstat})
                \end{minipg3}\\
                \>\>    int    \>  	{\fov inbcrv};\\
                \>\>    SISLCurve    \>  *{\fov vpcurv}[\,];\\
                \>\>    int    \>  	{\fov nctyp}[\,];\\
                \>\>    double    \>  {\fov epar}[\,];\\
                \>\>    double	\> {\fov astpar};\\
                \>\>    int    \>  	{\fov iopen};\\
                \>\>    int    \>  	{\fov iord2};\\
                \>\>    int    \>  	{\fov iflag};\\
                \>\>    SISLSurf    \>  **{\fov rsurf};\\
                \>\>    double 	\> **{\fov gpar};\\
                \>\>    int    \>  	*{\fov jstat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
        \>\>    {\fov inbcrv}\> - \>  \begin{minipg2}
                    set.
                               \end{minipg2}\\
        \>\>    {\fov vpcurv}\> - \>  \begin{minipg2}
                     Array (length inbcrv) of pointers to the
                       curves in the curve-set.
                               \end{minipg2}\\[0.8ex]
        \>\>    {\fov nctyp}\> - \>  \begin{minipg2}
                     Array (length inbcrv) containing the types
                       of curves in the curve-set.
                               \end{minipg2}\\[0.8ex]
                \>\>\>\> $=1$ \> : Ordinary curve.\\
                \>\>\>\> $=2$ \> : Knuckle curve. Treated as an ordinary curve.\\
                \>\>\>\> $=3$ \> : Tangent to next curve.\\
                \>\>\>\> $=4$ \> : Tangent to previous curve.\\
                \>\>\>\> ($=5$ \> : Second derivative to previous curve.)\\
                \>\>\>\> ($=6$ \> : Second derivative to next curve.)\\
                \>\>\>\> $=13$ \> : Curve giving start of tangent to next curve.\\
                \>\>\>\> $=14$ \> : Curve giving end of tangent to previous curve.\\
        \>\>    {\fov epar}\> - \>  \begin{minipg2}
                     Array containing the wanted parametrization. Only
                       parametervalues corresponding to position
                       curves are given. For closed curves, one additional
                       parameter value must be spesified. The last entry
                       contains the parametrization of the repeted start
                       curve. (if the endpoint is equal to the startpoint
                       of the interpolation the lenght of the array should
                       be equal to inpt1 also in the closed case). The
                       number of entries in the array is thus equal to
                       the number of position curves (number plus one
                       if the curve is closed).
                               \end{minipg2}\\
        \>\>    {\fov astpar}\> - \>  \begin{minipg2}
                    parameter for spline lofting direction.
                               \end{minipg2}\\
        \>\>    {\fov iopen}\> - \>  \begin{minipg2}
                     Flag saying whether the resulting surface should
                       be closed or open.
                               \end{minipg2}\\
        \>\>\>\>  $= 1$ \> : Open.\\
        \>\>\>\>  $= 0$ \> : Closed.\\
        \>\>\>\>  $= -1$ \> : Closed and periodic.\\
        \>\>    {\fov iord2}\> - \>  \begin{minipg2}
                    spline basis in the
                       lofting direction.
                               \end{minipg2}\\[0.8ex]
        \>\>    {\fov iflag}\> - \>  \begin{minipg2}
                     Flag saying whether the size of the tangents in the
                       derivative curves should be adjusted or not.
                               \end{minipg2}\\
                      \>\>\>\> $= 0$ \> : Do not adjust tangent sizes.\\
                      \>\>\>\> $= 1$ \> : Adjust tangent sizes.\\
\\
	\>Output Arguments:\\
        \>\>    {\fov rsurf}\> - \>  \begin{minipg2}
                     Pointer to the surface produced.
                               \end{minipg2}\\
        \>\>    {\fov gpar}  \> - \>
        \begin{minipg2}
          The input curves are constant parameter lines
          in the parameter-plane of the produced surface.
          The $i$-th element in this array contains the (constant) value
          of this parameter of the $i$-th. input curve.
        \end{minipg2}\\
        \>\>    {\fov jstat} \> - \> Status message\\
                \>\>\>\> $< 0$ \> : Error.\\
                \>\>\>\> $= 0$ \> : Ok.\\
                \>\>\>\> $> 0$ \> : Warning.\\
\\
EXAMPLE OF USE\\
		\>      \{ \\

                \>\>    int    \>  	{\fov inbcrv};\\
                \>\>    SISLCurve    \>  *{\fov vpcurv}[\,];\\
                \>\>    int    \>  	{\fov nctyp}[\,];\\
                \>\>    double    \>  {\fov epar}[\,];\\
                \>\>    double	\> {\fov astpar};\\
                \>\>    int    \>  	{\fov iopen};\\
                \>\>    int    \>  	{\fov iord2};\\
                \>\>    int    \>  	{\fov iflag};\\
                \>\>    SISLSurf    \>  **{\fov rsurf};\\
                \>\>    double 	\> **{\fov gpar};\\
                \>\>    int    \>  	*{\fov jstat};\\                \>\>    \ldots \\
        \>\>s1539(\begin{minipg4}
            {\fov inbcrv}, {\fov vpcurv}, {\fov nctyp}, {\fov epar}, {\fov astpar}, {\fov iopen}, {\fov iord2},
            {\fov iflag}, {\fov rsurf}, {\fov gpar}, {\fov jstat});
                \end{minipg4}\\
                \>\>    \ldots \\
		\>      \}
\end{tabbing}
