\subsection{Create a lofted surface from a set of B-spline
input curves.}
\funclabel{s1538}
\begin{minipg1}
  To create a lofted surface from a set of B-spline (i.e.\ NOT rational)
  input curves.
  The output is represented as a B-spline surface.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1538(\begin{minipg3}
          {\fov inbcrv}, {\fov vpcurv}, {\fov nctyp}, {\fov astpar}, {\fov iopen}, {\fov iord2},
          {\fov iflag}, {\fov rsurf}, {\fov gpar}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    int       \> {\fov inbcrv};\\
        \>\>    SISLCurve \> *{\fov vpcurv}[\,];\\
        \>\>    int       \> {\fov nctyp}[\,];\\
        \>\>    double    \> {\fov astpar};\\
        \>\>    int       \> {\fov iopen};\\
        \>\>    int       \> {\fov iord2};\\
        \>\>    int       \> {\fov iflag};\\
        \>\>    SISLSurf  \> **{\fov rsurf};\\
        \>\>    double    \> **{\fov gpar};\\
        \>\>    int       \> *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov inbcrv} \> - \> Number of B-spline curves in the curve set.\\
        \>\>    {\fov vpcurv} \> - \>
        \begin{minipg2}
          Array (length {\fov inbcrv}) of pointers to the
          curves in the curve-set.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov nctyp}  \> - \>
        \begin{minipg2}
          Array (length {\fov inbcrv}) containing the types
          of curves in the curve-set.
        \end{minipg2}\\[0.8ex]
                \>\>\>\> $=1$ \> : Ordinary curve.\\
                \>\>\>\> $=2$ \> : Knuckle curve. Treated as an ordinary curve.\\
                \>\>\>\> $=3$ \> : Tangent to next curve.\\
                \>\>\>\> $=4$ \> : Tangent to prior curve.\\
                \>\>\>\> ($=5$ \> : Second derivative to prior curve.)\\
                \>\>\>\> ($=6$ \> : Second derivative to next curve.)\\
                \>\>\>\> $=13$ \> : Curve giving start of tangent to next curve.\\
                \>\>\>\> $=14$ \> : Curve giving end of tangent to prior curve.\\
        \>\>    {\fov astpar} \> - \> Start parameter for spline lofting
                                      direction.\\
        \>\>    {\fov iopen} \> - \>
        \begin{minipg2}
          Flag telling if the resulting surface should be open, closed
          or periodic in the lofting direction (i.e.\ not the curve direction).
        \end{minipg2}\\[0.3ex]
        \>\>\>\>  $= 1$ \> : Open.\\
        \>\>\>\>  $= 0$ \> : Closed.\\
        \>\>\>\>  $= -1$ \> : Closed and periodic.\\
        \>\>    {\fov iord2} \> - \>
        \begin{minipg2}
          Maximal order of the surface in the lofting direction.
        \end{minipg2}\\[0.8ex]
\newpagetabs
        \>\>    {\fov iflag} \> - \>
        \begin{minipg2}
          Flag telling if the size of the tangents in the
          derivative curves should be adjusted or not.
        \end{minipg2}\\[0.3ex]
                      \>\>\>\> $= 0$ \> : Do not adjust tangent sizes.\\
                      \>\>\>\> $= 1$ \> : Adjust tangent sizes.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov rsurf} \> - \> Pointer to the B-spline surface produced.\\
        \>\>    {\fov gpar}  \> - \>
        \begin{minipg2}
          The input curves are constant parameter lines
          in the parameter-plane of the produced surface.
          The $i$-th element in this array contains the (constant) value
          of this parameter of the $i$-th. input curve.
        \end{minipg2}\\
        \>\>    {\fov jstat} \> - \> Status message\\
                \>\>\>\> $< 0$ \> : Error.\\
                \>\>\>\> $= 0$ \> : Ok.\\
                \>\>\>\> $> 0$ \> : Warning.\\
\\
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    int       \> {\fov inbcrv};\\
        \>\>    SISLCurve \> *{\fov vpcurv}[3];\\
        \>\>    int       \> {\fov nctyp}[3];\\
        \>\>    double    \> {\fov astpar};\\
        \>\>    int       \> {\fov iopen};\\
        \>\>    int       \> {\fov iord2};\\
        \>\>    int       \> {\fov iflag};\\
        \>\>    SISLSurf  \> *{\fov rsurf} = NULL;\\
        \>\>    double    \> *{\fov gpar} = NULL;\\
        \>\>    int       \> {\fov jstat} = 0;\\
        \>\>    \ldots \\
        \>\>s1538(\begin{minipg4}
          {\fov inbcrv}, {\fov vpcurv}, {\fov nctyp}, {\fov astpar}, {\fov iopen}, {\fov iord2},
          {\fov iflag}, \&{\fov rsurf}, \&{\fov gpar}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
