\subsection{Compute a curve using the input points as
controlling \mbox{vertices}, automatic parameterization.}
\funclabel{s1630}
\begin{minipg1}
  To compute a curve using the input points as controlling
  vertices. The distances between the points are used as
  parametrization.
  The output will be represented as a B-spline curve.
\end{minipg1}\\ \\
SYNOPSIS\\
        \>void s1630(\begin{minipg3}
          {\fov epoint}, {\fov inbpnt}, {\fov astpar}, {\fov iopen}, {\fov idim}, {\fov ik}, {\fov rc}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\> double \>  {\fov epoint}[\,];\\
        \>\> int    \>  {\fov inbpnt};\\
        \>\> double \>  {\fov astpar};\\
        \>\> int    \>  {\fov iopen};\\
        \>\> int    \>  {\fov idim};\\
        \>\> int    \>  {\fov ik};\\
        \>\> SISLCurve \> **{\fov rc};\\
        \>\> int    \>  *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov epoint} \> - \>
        \begin{minipg2}
          The array containing the points to be used as
          controlling vertices of the B-spline curve.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov inbpnt} \> - \> No. of points in epoint.\\
        \>\>    {\fov astpar} \> - \>
        \begin{minipg2}
          Parameter value to be used at the start of the curve.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov iopen} \> - \>
        \begin{minipg2}
          Open/closed/periodic condition.
        \end{minipg2}\\[0.8ex]
            \>\>\>\> $=-1$ \> : Closed and periodic.\\
            \>\>\>\> $=0$  \> : Closed.\\
            \>\>\>\> $=1$  \> : Open.\\
        \>\>    {\fov idim} \> - \> The dimension of the space.\\
        \>\>    {\fov ik}   \> - \> The order of the spline curve to be produced.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov rc} \> - \> Pointer to the B-spline curve.\\
        \>\>    {\fov jstat}\> - \> Status message\\
                \>\>\>\>\> $< 0$ : Error.\\
                \>\>\>\>\> $= 0$ : Ok.\\
                \>\>\>\>\> $> 0$ : Warning.\\
\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    double \> {\fov epoint}[30];\\
        \>\>    int    \> {\fov inbpnt} = 10;\\
        \>\>    double \> {\fov astpar} = 0.0;\\
        \>\>    int    \> {\fov iopen} = 1;\\
        \>\>    int    \> {\fov idim} = 3;\\
        \>\>    int    \> {\fov ik} = 4;\\
        \>\>    SISLCurve \> *{\fov rc} = NULL;\\
        \>\>    int    \> {\fov jstat};\\
        \>\>    \ldots \\
        \>\>s1630(\begin{minipg4}
          {\fov epoint}, {\fov inbpnt}, {\fov astpar}, {\fov iopen}, {\fov idim}, {\fov ik}, \&{\fov rc}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
