\subsection{Join two curves at closest ends.}
\funclabel{s1716}
\begin{minipg1}
  To join two curves at the ends that lie closest to each other, if the
  distance between the ends is less than the tolerance {\fov epsge}. If
  {\fov curve1} is to be joined at the start, the direction of the curve is turned.
  If {\fov curve2} is to be joined at the end, the direction of this
  curve is turned. This means that {\fov curve1} always makes up the
  first part of the new curve. If {\fov epsge} is positive, but smaller
  than the smallest distance between the ends of the two curves, a NULL
  pointer is returned.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1716(\begin{minipg3}
        {\fov curve1}, {\fov curve2}, {\fov epsge}, {\fov newcurve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve1};\\
                \>\>    SISLCurve       \>      *{\fov curve2};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    SISLCurve       \>      **{\fov newcurve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve1}   \> - \> First curve to join.\\
        \>\>    {\fov curve2}   \> - \> Second curve to join.\\
        \>\>    {\fov epsge}    \> - \> \begin{minipg2}
                                The curves are to be joined if {\fov epsge} is
                                greater than or equal to the distance
                                between the ends lying closest to each
                                other. If {\fov epsge} is negative, the
                                curves are automatically joined.
                                \end{minipg2}\\[0.3ex]
\\
        \>Output Arguments:\\
        \>\>    {\fov newcurve}\> - \>\begin{minipg2}
                                The new joined curve.
                                \end{minipg2}\\
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\ %\newpagetabs
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov curve1};\\
                \>\>    SISLCurve       \>      *{\fov curve2};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    SISLCurve       \>      *{\fov newcurve};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1716(\begin{minipg4}
                {\fov curve1}, {\fov curve2}, {\fov epsge}, \&{\fov newcurve}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
