\subsection{Local iteration to closest point bewteen point and surface.}
\funclabel{s1775}
\begin{minipg1}
Newton iteration on the distance function between
               a surface and a point, to find a closest point or an
               intersection point.
               If a bad choice for the guess parameters is given in, the
               iteration may end at a local, not global closest point.
\end{minipg1} \\ \\
SYNOPSIS\\
        \> void s1775(\begin{minipg3}
            {\fov surf},  {\fov point},  {\fov dim},  {\fov epsge},  {\fov start},  {\fov end},  {\fov guess},  {\fov clpar},  {\fov stat})
                \end{minipg3}\\
                \>\>    SISLSurf \> *{\fov surf};\\
                \>\>    double \> {\fov point}[\,];\\
                \>\>    int \> {\fov dim};\\
                \>\>    double \> {\fov epsge};\\
                \>\>    double \> {\fov start}[\,];\\
                \>\>    double \> {\fov end}[\,];\\
                \>\>    double \> {\fov guess}[\,];\\
                \>\>    double \> {\fov clpar}[\,];\\
                \>\>    int \> *{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
        \>\>    {\fov surf}\> - \>  \begin{minipg2}
                     The surface in the closest point problem.
                               \end{minipg2}\\
        \>\>    {\fov point}\> - \>  \begin{minipg2}
                     The point in the closest point problem.
                               \end{minipg2}\\
        \>\>    {\fov dim}\> - \>  \begin{minipg2}
                     Dimension of the geometry.
                               \end{minipg2}\\
        \>\>    {\fov epsge}\> - \>  \begin{minipg2}
                     Geometry resolution.
                               \end{minipg2}\\
        \>\>    {\fov start}\> - \>  \begin{minipg2}
                     Surface parameters giving the start of the search
                        area (umin, vmin).
                               \end{minipg2}\\
        \>\>    {\fov end}\> - \>  \begin{minipg2}
                     Surface parameters giving the end of the search
                        area (umax, vmax).
                               \end{minipg2}\\
        \>\>    {\fov guess}\> - \>  \begin{minipg2}
                     Surface guess parameters for the closest point
                        iteration.
                               \end{minipg2}\\
\\
	\>Output Arguments:\\
        \>\>    {\fov clpar}\> - \>  \begin{minipg2}
                     Resulting surface parameters from the iteration.
                               \end{minipg2}\\
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : A minimum distance found.\\
                \>\>\>\>\>              $= 0$   : Intersection found.\\
                \>\>\>\>\>              $< 0$   : Error.\\
\\
EXAMPLE OF USE\\
		\>      \{ \\

                \>\>    SISLSurf \> *{\fov surf};\\
                \>\>    double \> {\fov point}[\,];\\
                \>\>    int \> {\fov dim};\\
                \>\>    double \> {\fov epsge};\\
                \>\>    double \> {\fov start}[\,];\\
                \>\>    double \> {\fov end}[\,];\\
                \>\>    double \> {\fov guess}[\,];\\
                \>\>    double \> {\fov clpar}[\,];\\
                \>\>    int \> *{\fov stat};\\                \>\>    \ldots \\
        \>\>s1775(\begin{minipg4}
            {\fov surf},  {\fov point},  {\fov dim},  {\fov epsge},  {\fov start},  {\fov end},  {\fov guess},  {\fov clpar},  {\fov stat});
                \end{minipg4}\\
                \>\>    \ldots \\
		\>      \}
\end{tabbing}
