\section{Find the Absolute Extremals of a Surface.}
\funclabel{s1921}
\begin{minipg1}
  Find the absolute extremal points/curves of a surface along a given direction.
\end{minipg1}\\ \\
SYNOPSIS\\
        \>void s1921(\begin{minipg3}
          {\fov ps1}, {\fov edir}, {\fov idim}, {\fov aepsco}, {\fov aepsge}, {\fov jpt}, {\fov gpar}, {\fov jcrv}, {\fov wcurve}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    SISLSurf  \>  *{\fov ps1};\\
        \>\>    double    \>  {\fov edir}[\,];\\
        \>\>    int       \>  {\fov idim};\\
        \>\>    double    \>  {\fov aepsco};\\
        \>\>    double    \>  {\fov aepsge};\\
        \>\>    int       \>  *{\fov jpt};\\
        \>\>    double    \>  **{\fov gpar};\\
        \>\>    int       \>  *{\fov jcrv};\\
        \>\>    SISLIntcurve \> ***{\fov wcurve};\\
        \>\>    int       \>  *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov ps1}\> - \>  \begin{minipg2}
                     Pointer to the surface.
                               \end{minipg2}\\
        \>\>    {\fov edir}\> - \>
        \begin{minipg2}
          The direction in which the extremal point(s)
          and/or interval(s) are to be calculated. If
          $idim=1$ a positive value indicates the maximum
          of the function and a negative value
          the minimum. If the dimension is greater that
          1 the array contains the coordinates of the
          direction vector.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov idim}\> - \>  \begin{minipg2}
                     Dimension of the space in which the vector {\fov edir}
                       lies.
                               \end{minipg2}\\
        \>\>    {\fov aepsco}\> - \>  \begin{minipg2}
                     Computational resolution (not used).
                               \end{minipg2}\\
        \>\>    {\fov aepsge}\> - \>  \begin{minipg2}
                     Geometry resolution.
                               \end{minipg2}\\
\\
        \>Output Arguments:\\
        \>\>    {\fov jpt}\> - \>  \begin{minipg2}
                     Number of single extremal points.
                               \end{minipg2}\\
        \>\>    {\fov gpar}\> - \>
        \begin{minipg2}
          Array containing the parameter values of the
          single extremal points in the parameter
          area of the surface. The points lie continuous.
          Extremal curves are stored in {\fov wcurve}.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov jcrv}\> - \>  \begin{minipg2}
                     Number of extremal curves.
                               \end{minipg2}\\
        \>\>    {\fov wcurve}\> - \>
        \begin{minipg2}
          Array containing descriptions of the extremal
          curves. The curves are only described by points
          in the parameter area. The curve-pointers point
          to nothing.
        \end{minipg2}\\[0.8ex]
\newpagetabs
        \>\>    {\fov jstat}     \> - \> Status messages\\
                \>\>\>\>              $> 0$ \> : Warning.\\
                \>\>\>\>              $= 0$ \> : Ok.\\
                \>\>\>\>              $< 0$ \> : Error.\\
\\
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    SISLSurf  \>  *{\fov ps1};\\
        \>\>    double    \>  {\fov edir}[3];\\
        \>\>    int       \>  {\fov idim} = 3;\\
        \>\>    double    \>  {\fov aepsco};\\
        \>\>    double    \>  {\fov aepsge};\\
        \>\>    int       \>  {\fov jpt} = 0;\\
        \>\>    double    \>  *{\fov gpar} = NULL;\\
        \>\>    int       \>  {\fov jcrv} = 0;\\
        \>\>    SISLIntcurve \> **{\fov wcurve} = NULL;\\
        \>\>    int       \>  {\fov jstat} = 0;\\
        \>\>    \ldots \\
        \>\>s1921(\begin{minipg4}
          {\fov ps1}, {\fov edir}, {\fov idim}, {\fov aepsco}, {\fov aepsge}, \&{\fov jpt}, \&{\fov gpar}, \&{\fov jcrv}, \&{\fov wcurve}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
