\section{Find the Absolute Extremals of a Curve.}
\funclabel{s1920}
\begin{minipg1}
  Find the absolute extremal points/intervals of a curve relative to a
  given direction.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1920(\begin{minipg3}
        {\fov curve}, {\fov dir}, {\fov dim}, {\fov epsco}, {\fov epsge}, {\fov numintpt},
        {\fov intpar},\\ {\fov numintcu}, {\fov intcurve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov dir}[\,];\\
                \>\>    int     \>      {\fov dim};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov numintpt};\\
                \>\>    double  \>      **{\fov intpar};\\
                \>\>    int     \>      *{\fov numintcu};\\
                \>\>    SISLIntcurve \> ***{\fov intcurve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve}    \> - \> Pointer to the curve.\\
        \>\>    {\fov dir}      \> - \> \begin{minipg2}
                                The direction in which the extremal point(s)
                                and/or interval(s) are to be
                                calculated. If $dim=1$, a positive value
                                indicates the maximum of the
                                function and a negative value the minimum.
                                If the dimension is greater than 1, the array
                                contains the coordinates of the direction vector.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov dim}      \> - \> \begin{minipg2}
                                Dimension of the space in which the
                                curve and {\fov dir} lie.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov epsco}    \> - \> Computational resolution (not used).\\
        \>\>    {\fov epsge}    \> - \> Geometry resolution.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov numintpt}\> - \>  Number of single extremal points.\\
        \>\>    {\fov intpar}   \> - \> \begin{minipg2}
                                Array containing the parameter values of the
                                single extremal points in the parameter
                                interval of the curve. The points lie in sequence.
                                Extremal curves are stored in intcurve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numintcu}\> - \>  Number of extremal curves.\\
        \>\>    {\fov intcurve}\> - \>  \begin{minipg2}
                                Array of pointers to the SISLIntcurve objects
                                containing descriptions of the extremal
                                curves. The curves are only described by
                                start points and end points in
                                the parameter interval of the curve. The
                                curve pointers point to nothing.
                                \end{minipg2}\\[0.3ex]
\newpagetabs
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : Warning.\\
                \>\>\>\>\>              $= 0$   : Ok.\\
                \>\>\>\>\>              $< 0$   : Error.\\
\\
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov curve}; \,/* Must be defined */\\
                \>\>    double  \>      {\fov dir}[3]; \, /* Must be defined */\\
                \>\>    int     \>      {\fov dim} = 3;\\
                \>\>    double  \>      {\fov epsco} = 1.0e-9; /* Not used */\\
                \>\>    double  \>      {\fov epsge} = 1.0e-6;\\
                \>\>    int     \>      {\fov numintpt} = 0;\\
                \>\>    double  \>      *{\fov intpar} =  NULL;\\
                \>\>    int     \>      {\fov numintcu} = 0;\\
                \>\>    SISLIntcurve \> **{\fov intcurve} = NULL;\\
                \>\>    int     \>      {\fov stat} = 0;\\
                \>\>    \ldots \\
        \>\>s1920(\begin{minipg4}
                {\fov curve}, {\fov dir}, {\fov dim}, {\fov epsco}, {\fov epsge}, \&{\fov numintpt},
                \&{\fov intpar}, \&{\fov numintcu}, \&{\fov intcurve}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
