\subsection{Find the closest point between a curve and a point.}
\funclabel{s1953}
\begin{minipg1}
  Find the closest points between a curve and a point.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1953(\begin{minipg3}
        {\fov curve}, {\fov point}, {\fov dim}, {\fov epsco}, {\fov epsge}, {\fov numintpt},
        {\fov intpar},\linebreak {\fov numintcu}, {\fov intcurve}, {\fov jstat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov point}[\,];\\
                \>\>    int     \>      {\fov dim};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov numintpt};\\
                \>\>    double  \>      **{\fov intpar};\\
                \>\>    int     \>      *{\fov numintcu};\\
                \>\>    SISLIntcurve \> ***{\fov intcurve};\\
                \>\>    int     \>      *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve}    \> - \> \begin{minipg2}
                                Pointer to the curve in the closest point problem.
                                \end{minipg2}\\
        \>\>    {\fov point}    \> - \> \begin{minipg2}
                                The point in the closest point problem.
                                \end{minipg2}\\
        \>\>    {\fov dim}      \> - \> \begin{minipg2}
                                Dimension of the space in which the
                                curve and point lie.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov epsco}    \> - \> Computational resolution (not used).\\
        \>\>    {\fov epsge}    \> - \> Geometry resolution.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov numintpt}\> - \>  Number of single closest points.\\
        \>\>    {\fov intpar}   \> - \> \begin{minipg2}
                                Array containing the parameter values of the
                                single closest points in the parameter
                                interval of the curve. The points lie in sequence.
                                Closest curves are stored in intcurve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numintcu}\> - \>  Number of closest curves.\\
        \>\>    {\fov intcurve}\> - \>  \begin{minipg2}
                                Array of pointers to the SISLIntcurve objects
                                containing descriptions of the closest
                                curves. The curves are only described by
                                start points and end points in
                                the parameter interval of the curve. The
                                curve pointers point to nothing.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov jstat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    SISLCurve \> *{\fov curve};\\
        \>\>    double  \>   {\fov point}[3];\\
        \>\>    int     \>   {\fov dim} = 3;\\
        \>\>    double  \>   {\fov epsco};\\
        \>\>    double  \>   {\fov epsge};\\
        \>\>    int     \>   {\fov numintpt};\\
        \>\>    double  \>   *{\fov intpar};\\
        \>\>    int     \>   {\fov numintcu};\\
        \>\>    SISLIntcurve \> **{\fov intcurve};\\
        \>\>    int     \>   {\fov jstat};\\
        \>\>    \ldots \\
        \>\>s1953(\begin{minipg4}
          {\fov curve}, {\fov point}, {\fov dim}, {\fov epsco}, {\fov epsge}, \&{\fov numintpt},
          \&{\fov intpar},\linebreak \&{\fov numintcu}, \&{\fov intcurve}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
