\subsection{Curvature on a uniform grid of a NURBS surface.}
\funclabel{s2540}
\begin{minipg1}
To compute a set of curvature values on a uniform grid 
            in a selected subset of the parameter domain of a NURBS surface.
\end{minipg1} \\ \\
SYNOPSIS\\
        \> void s2540(\begin{minipg3}
            {\fov surf}, {\fov curvature\_type},  {\fov export\_par\_val},  {\fov pick\_subpart}, boundary[],  {\fov n\_u},  {\fov n\_v}, 
       {\fov garr},  {\fov stat})
                \end{minipg3}\\
                \>\>    SISLSurf \> *{\fov surf};\\
                \>\>    int \> {\fov curvature\_type};\\
                \>\>    int \> {\fov export\_par\_val};\\
                \>\>    int \> {\fov pick\_subpart};\\
                \>\>    double \> {\fov boundary}[\,];\\
                \>\>    int \> {\fov n\_u};\\
                \>\>    int \> {\fov n\_v};\\
                \>\>    double \> **{\fov garr};\\
                \>\>    int \> *{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
        \>\>    {\fov surf}\> - \>  \begin{minipg2}
                     The surface to evaluate.
                               \end{minipg2}\\[0.8ex]
        \>\>    {\fov curvature}\> - \>  \begin{minipg2}
                     The type of curvature:
                               \end{minipg2}\\[0.8ex]
        \>\>\>\> $0$  \> : Gaussian curvature.\\
        \>\>\>\> $1$  \> : Mean curvature.\\
        \>\>\>\> $2$  \> : Absolute curvature.\\
        \>\>\>\> $3$  \> : Total curvature.\\
        \>\>\>\> $4$  \> : Second order Mehlum curvature.\\
        \>\>\>\> $5$  \> : Third order Mehlum curvature.\\
        \>\>    {\fov export}\> - \>  \begin{minipg2}
                     Flag indicating whether the parameter values
                            of the grid points are to be exported:
                               \end{minipg2}\\[0.8ex]
        \>\>\>\> $0$  \> : False, do not export parameter values.\\
        \>\>\>\> $1$  \> : True, do export parameter values.\\
        \>\>    {\fov pick}\> - \>  \begin{minipg2}
                     Flag indicating whether the grid is to be
                            calculated on a subpart of the surface:
                               \end{minipg2}\\[0.8ex]
        \>\>\>\> $0$  \> : False, calculate grid on the complete surface.\\
        \>\>\>\> $1$  \> : True, calculate grid on a part of the surface.\\
        \>\>    {\fov boundary}\> - \>  \begin{minipg2}
                     A rectangular subset of the parameter domain.
                               \end{minipg2}\\[0.8ex]
        \>\>\>\> $0$  \> : Minmum value in the first parameter.\\
        \>\>\>\> $1$  \> : Minmum value in the second parameter.\\
        \>\>\>\> $2$  \> : Maximum value in the first parameter.\\
        \>\>\>\> $3$  \> : Maximum value in the second parameter.\\
        \>\>\>\> \begin{minipg2}
                            ONLY USED WHEN {\fov pick\_subpart} $= 1$.
                            If {\fov pick\_subpart} $= 0$
                            the parameter area of surf is returned here.
                               \end{minipg2}\\[0.8ex]
        \>\>    {\fov n\_u}\> - \>  \begin{minipg2}
                     Number of segments in the first parameter.
                               \end{minipg2}\\[0.8ex]
        \>\>    {\fov n\_v}\> - \>  \begin{minipg2}
                     Number of segments in the second parameter.
                               \end{minipg2}\\[0.8ex]
\\
	\>Output Arguments:\\
        \>\>    {\fov garr}\> - \>  \begin{minipg2}
                     Array containing the computed values on the grid.
		     The allocation is done internally and the dimension 
		    is  3*(n\_u+1)*(n\_v+1) if export\_par\_val is true,
		     and (n\_u+1)*(n\_v+1) if export\_par\_val is false.
                     Each gridpoint consists of a triple 
                     $(u_i,v_j,curvature(u_i,v_j))$ or only $curvature(u_,v_j)$.
		     The sequence runs first in the first parameter.
                              \end{minipg2}\\[0.8ex]
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>   $> 0$  \> : Warning.\\
                \>\>\>\>   $= 0$  \> : Ok.\\
                \>\>\>\>   $< 0$  \> : Error.\\
\\
EXAMPLE OF USE\\
		\>      \{ \\
                \>\>    SISLSurf \> *{\fov surf};\\
                \>\>    int \> {\fov curvature\_type};\\
                \>\>    int \> {\fov export\_par\_val};\\
                \>\>    int \> {\fov pick\_subpart};\\
                \>\>    double \> {\fov boundary}[\,];\\
                \>\>    int \> {\fov n\_u};\\
                \>\>    int \> {\fov n\_v};\\
                \>\>    double \> **{\fov garr};\\ 
                \>\>    int \> *{\fov stat};\\                \>\>    \ldots \\
        \>\>s2540(\begin{minipg4}
            {\fov surf}, {\fov curvature\_type}, {\fov export\_par\_val}, {\fov pick\_subpart}, {\fov boundary}[], {\fov n\_u}, {\fov n\_v}, 
       {\fov garr}, {\fov stat});
                \end{minipg4}\\
                \>\>    \ldots \\
		\>      \}
\end{tabbing}
