\typelabel{SISLCurve}
  \>int         \>{\fov ik};     \>\>Order of curve. \\
  \>int         \>{\fov in};     \>\>Number of vertices. \\
  \>double      \>*{\fov et};    \>\>Pointer to the knot vector.  \\
  \>double      \>*{\fov ecoef}; \>\> \begin{minipg2}
                         Pointer to the array containing
                         non-rational vertices, size $in\times idim$.
                                      \end{minipg2}\\[0.8ex]
 \>double       \>*{\fov rcoef}; \>\> \begin{minipg2}
                         Pointer to the array of rational
                         vertices and weights, size $in\times (idim+1)$.
                                      \end{minipg2}\\[0.8ex]
 \>int  \>{\fov ikind};  \>\>Type of curve\\
        \>\>\>\>\>     $= 1$ :\> Polynomial B-spline curve.\\
        \>\>\>\>\>     $= 2$ :\> Rational B-spline (nurbs) curve.\\
        \>\>\>\>\>     $= 3$ :\> Polynomial Bezier curve.\\
        \>\>\>\>\>     $= 4$ :\> Rational Bezier curve.\\
  \>int         \>{\fov idim};   \>\>Dimension of the space in which the
                                        curve lies.  \\
  \>int         \>{\fov icopy};  \>\> \begin{minipg2}
                        Indicates whether the arrays of the curve are
                       allocated and copied or referenced by creation of the curve.
                                \end{minipg2}\\[0.3ex]
        \>\>\>\>\>     $= 0$ :\>        \begin{minipg5}
                                 Pointer set to input arrays. The
                                arrays are not deleted by freeCurve.
                                        \end{minipg5}\\[0.3ex]
        \>\>\>\>\>     $= 1$ :\>        \begin{minipg5}
                                Array allocated and copied. The
                                arrays are deleted by freeCurve.
                                        \end{minipg5}\\[0.3ex]
        \>\>\>\>\>     $= 2$ :\>        \begin{minipg5}
                                Pointer set to input arrays,
                             but are to be treated as copied. The
                                arrays are deleted by freeCurve.
                                        \end{minipg5}\\[0.3ex]
  \>SISLdir     \>*{\fov pdir}; \>\>\begin{minipg2}
                        Pointer to a SISLdir object used for storing curve direction.
                                \end{minipg2}\\[0.8ex]
  \>SISLbox     \>*{\fov pbox}; \>\>\begin{minipg2}
                        Pointer to a SISLbox object used for storing the surrounding boxes.
                                \end{minipg2}\\[0.8ex]
  \>int         \>{\fov cuopen}; \>\>       Open/closed/periodic flag. \\
        \>\>\>\>\>     $=-1$ \> : \begin{minipg5}
                                Closed curve with periodic (cyclic)
                                parameterization and overlapping
                                end vertices.
                                   \end{minipg5}\\[0.3ex]
        \>\>\>\>\>     $=0$ \>  : \begin{minipg5}
                                Closed curve with k-tuple end knots and
                                coinciding start/end vertices.
                                  \end{minipg5}\\[0.3ex]
        \>\>\>\>\>     $=1$ \>  : Open curve (default).\\
\end{tabbing}
