\subsection{Insert a given set of knots, in each parameter direction, into the description of a surface.}
\funclabel{s1025}
\begin{minipg1}
  Insert a given set of knots in each parameter direction
  into the description of a surface.\\
  NOTE       : When the surface is periodic in one direction, the input
               parameter values in this direction
               must lie in the half-open interval $[et[kk-1], et[kn)$, the function
               will automatically update the extra knots and
               coeffisients.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1025(\begin{minipg3}
          {\fov ps},  {\fov epar1},  {\fov inpar1},  {\fov epar2},  {\fov inpar2},  {\fov rsnew},  {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    SISLSurf \> *{\fov ps};\\
        \>\>    double   \> {\fov epar1}[\,];\\
        \>\>    int      \> {\fov inpar1};\\
        \>\>    double   \> {\fov epar2}[\,];\\
        \>\>    int      \> {\fov inpar2};\\
        \>\>    SISLSurf \> **{\fov rsnew};\\
        \>\>    int      \> *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov ps}\> - \>  \begin{minipg2}
                     Surface to be refined.
                               \end{minipg2}\\
        \>\>    {\fov epar1}\> - \>  \begin{minipg2}
                     Knots to insert in first parameter direction.
                               \end{minipg2}\\
        \>\>    {\fov inpar1}\> - \>  \begin{minipg2}
                     Number of new knots in first parameter direction.
                               \end{minipg2}\\
        \>\>    {\fov epar2}\> - \>  \begin{minipg2}
                     Knots to insert in second parameter direction.
                               \end{minipg2}\\
        \>\>    {\fov inpar2}\> - \>  \begin{minipg2}
                     Number of new knots in second parameter direction.
                               \end{minipg2}\\
\\
        \>Output Arguments:\\
        \>\>    {\fov rsnew}\> - \>  \begin{minipg2}
                     The new, refined surface.
                                \end{minipg2}\\
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>      $> 0$ : \>      Warning.\\
                \>\>\>\>\>      $= 0$ : \>      Ok.\\
                \>\>\>\>\>      $< 0$ : \>      Error.\\
\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    SISLSurf \> *{\fov ps};\\
        \>\>    double   \> {\fov epar1}[3];\\
        \>\>    int      \> {\fov inpar1} = 3;\\
        \>\>    double   \> {\fov epar2}[4];\\
        \>\>    int      \> {\fov inpar2} = 4;\\
        \>\>    SISLSurf \> *{\fov rsnew} = NULL;\\
        \>\>    int      \> {\fov jstat} = 0;\\
        \>\>    \ldots \\
        \>\>s1025(\begin{minipg4}
          {\fov ps},  {\fov epar1},  {\fov inpar1},  {\fov epar2},  {\fov inpar2},  \&{\fov rsnew},  \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
