\subsection{Draw constant parameter lines in a
surface bounded by a closed curve in the parameter plane of the surface.}
\funclabel{s1238}
\begin{minipg1}
  Draw constant parameter lines in a surface. The lines are limited by a closed
  curve lying in the parameter plane of the surface, i.e.\ a 2D curve.
  All lines are drawn as piecewise straight lines. Also see NOTE!
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1238(\begin{minipg3}
                {\fov surf}, {\fov curve}, {\fov numline1}, {\fov numline2}, {\fov epsco}, {\fov epsge}, {\fov stat})
                \end{minipg3}\\[0.3ex]

                \>\>    SISLSurf        \>      *{\fov surf};\\
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    int     \>      {\fov numline1};\\
                \>\>    int     \>      {\fov numline2};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov surf}\> - \>      \begin{minipg2}
                                Pointer to the surface.
                                \end{minipg2}\\
        \>\>    {\fov curve}\> - \>     \begin{minipg2}
                                The 2D curve, in the parameter plane of
                                the surface, bounding the part of the
                                surface that is to be drawn.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numline1}\> - \>  \begin{minipg2}
                                Number of constant parameter lines to be drawn in the first
                                parameter direction.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov numline2}\> - \>  \begin{minipg2}
                                Number of constant parameter lines to be drawn in the
                                second parameter direction.
                                \end{minipg2} \\[0.3ex]
        \>\>    {\fov epsco}\> - \>     \begin{minipg2}
                                Not in use!
                                \end{minipg2}\\
        \>\>    {\fov epsge}\> - \>     \begin{minipg2}
                                The maximal distance allowed between the drawn curves
                                and the surface.
                                \end{minipg2}\\[0.8ex]
        \>Output Arguments:\\
        \>\>    {\fov sta}t     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\
NOTE\\
\>\begin{minipg6}
This function calls s6drawseq() which
is device dependent. Before using the function make sure
you have a version of s6drawseq()
interfaced to your graphic package.
More about s6drawseq() on page~\pageref{s6drawseq}.
\end{minipg6}
\newpagetabs
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLSurf        \>      *{\fov surf};\\
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    int     \>      {\fov numline1};\\
                \>\>    int     \>      {\fov numline2};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1238(\begin{minipg4}
                        {\fov surf}, {\fov curve}, {\fov numline1}, {\fov numline2}, {\fov epsco}, {\fov epsge}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \} \\
\end{tabbing}
