\subsection{Draw constant parameter lines in a surface
using piecewise straight lines.}
\funclabel{s1237}
\begin{minipg1}
  Draw constant parameter lines in a surface.
  The distance between the surface and the
  straight lines is less than a tolerance epsge. Also see NOTE!
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1237(\begin{minipg3}
                                {\fov surf}, {\fov numline1}, {\fov numline2}, {\fov epsge}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLSurf        \>      *{\fov surf};\\
                \>\>    int     \>      {\fov numline1};\\
                \>\>    int     \>      {\fov numline2};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov surf}\> - \>      \begin{minipg2}
                                Pointer to the surface.
                                \end{minipg2}\\
        \>\>    {\fov numline1}\> - \>  \begin{minipg2}
                                Number of constant parameter lines to be drawn in the first
                                parameter direction.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov numline2}\> - \>  \begin{minipg2}
                                Number of constant parameter lines to be drawn in the
                                second parameter direction.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov epsge}\> - \>     \begin{minipg2}
                                The maximal distance allowed between the drawn curves
                                and the surface.
                                \end{minipg2} \\[0.8ex]
\\
        \>Output Arguments:\\
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\
NOTE\\
\>\begin{minipg6}
This function calls s6drawseq() which
is device dependent. Before using the function make sure
you have a version of s6drawseq()
interfaced to your graphic package.
More about s6drawseq() on page~\pageref{s6drawseq}.
\end{minipg6}
\newpagetabs
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLSurf        \>      *{\fov surf};\\
                \>\>    int     \>      {\fov numline1};\\
                \>\>    int     \>      {\fov numline2};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1237(\begin{minipg4}
                        {\fov surf}, {\fov numline1}, {\fov numline2}, {\fov epsge}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
