\section{Extend a B-spline Curve.}
\funclabel{s1233}
\begin{minipg1}
  To extend a B-spline curve (i.e.\ NOT rationals) at the start and/or
  the end of the curve by continuing the polynomial behaviour of the
  curve.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1233(\begin{minipg3}
          {\fov pc}, {\fov afak1}, {\fov afak2}, {\fov rc}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    SISLCurve \>  *{\fov pc};\\
        \>\>    double    \>  {\fov afak1};\\
        \>\>    double    \>  {\fov afak2};\\
        \>\>    SISLCurve \>  **{\fov rc};\\
        \>\>    int       \>  *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov pc}    \> - \>
        \begin{minipg2}
          Pointer to the B-spline curve to be extended.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov afak1} \> - \>
        \begin{minipg2}
          How much the curve is to be stretched at the
          start of the curve. The length of the stretched
          curve will be equal to $(1+afak1)$ times the
          input curve. $afak1\geq 0$ and will be set to 0 if
          negative.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov afak2} \> - \>
        \begin{minipg2}
          How much the curve is to be stretched at the
          end of the curve. The length of the stretched
          curve will be equal to $(1+afak2)$ times the
          input curve. $afak2\geq 0$ and will be set to 0 if
          negative.
        \end{minipg2}\\[0.8ex]
\\
        \>Output Arguments:\\
        \>\>    {\fov rc}    \> - \> Pointer to the extended B-spline curve.\\
        \>\>    {\fov jstat} \> - \> Status message\\
                \>\>\>\>\> $< 0$ : Error.\\
                \>\>\>\>\> $= 0$ : Ok.\\
                \>\>\>\>\> $= 1$ : \begin{minipg5}
                                     Stretching factors less than 0
                                     -- readjusted factor(s)
                                     have been used.
                                   \end{minipg5}\\[0.3ex]
                \>\>\>\>\> $> 0$ : Warning.\\
\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    SISLCurve \>  *{\fov pc};\\
        \>\>    double    \>  {\fov afak1};\\
        \>\>    double    \>  {\fov afak2};\\
        \>\>    SISLCurve \>  *{\fov rc} = NULL;\\
        \>\>    int       \>  {\fov jstat} = 0;\\
        \>\>    \ldots \\
        \>\>s1233(\begin{minipg4}
          {\fov pc}, {\fov afak1}, {\fov afak2}, \&{\fov rc}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
