\subsection{Convert a surface/line intersection into a two-dimensional surface/origo intersection}
\funclabel{s1328}
\begin{minipg1}
Put the equation of the surface pointed at by psold
               into two planes given by the point epoint and the normals
               enorm1 and enorm2. The result is an equation where the 
               new two-dimensional surface rsnew is to be equal to origo.
\end{minipg1} \\ \\
SYNOPSIS\\
        \> void s1328(\begin{minipg3}
            {\fov psold}, {\fov epoint}, {\fov enorm1}, {\fov enorm2}, {\fov idim}, {\fov rsnew}, {\fov jstat})
                \end{minipg3}\\
                \>\>    SISLSurf    \>  *{\fov psold};\\
                \>\>    double \> epoint[\,];\\
                \>\>    double \> enorm1[\,];\\
                \>\>    double \> enorm2[\,];\\
                \>\>    int    \>  {\fov idim};\\
                \>\>    SISLSurf    \>  **{\fov rsnew};\\
                \>\>    int    \>  *{\fov jstat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
        \>\>    {\fov psold}\> - \>  \begin{minipg2}
                     Pointer to input surface.
                               \end{minipg2}\\
        \>\>    {\fov epoint}\> - \>  \begin{minipg2}
                     SISLPoint in the planes.
                               \end{minipg2}\\
        \>\>    {\fov enorm1}\> - \>  \begin{minipg2}
                     Normal to the first plane.
                               \end{minipg2}\\
        \>\>    {\fov enorm2}\> - \>  \begin{minipg2}
                     Normal to the second plane.
                               \end{minipg2}\\
        \>\>    {\fov idim}\> - \>  \begin{minipg2}
                     Dimension of the space in which the planes lie.
                               \end{minipg2}\\
\\
	\>Output Arguments:\\
        \>\>    {\fov rsnew}\> - \>  \begin{minipg2}
                    dimensional surface.
                               \end{minipg2}\\
        \>\>    {\fov jstat}\> - \> status messages  \\
	            \>\>\>\>\>          $ > 0 $      : warning\\
		    \>\>\>\>\>          $ = 0 $      : ok \\
		    \>\>\>\>\>          $ < 0 $      : error \\
\\
EXAMPLE OF USE\\
		\>      \{ \\

                \>\>    SISLSurf    \>  *{\fov psold};\\
                \>\>    double \> epoint[\,];\\
                \>\>    double \> enorm1[\,];\\
                \>\>    double \> enorm2[\,];\\
                \>\>    int    \>  {\fov idim};\\
                \>\>    SISLSurf    \>  **{\fov rsnew};\\
                \>\>    int    \>  *{\fov jstat};\\                \>\>    \ldots \\
        \>\>s1328(\begin{minipg4}
            {\fov psold}, {\fov epoint}, {\fov enorm1}, {\fov enorm2}, {\fov idim}, {\fov rsnew}, {\fov jstat});
                \end{minipg4}\\
                \>\>    \ldots \\
		\>      \}
\end{tabbing}
