\subsection{Spline interpolation automatic paramete\-risation.}
\funclabel{s1334}
\begin{minipg1}
To calculate a B-spline curve interpolating a set of points. Each
point can be assigned a tangent (derivative). The curve can be closed
or open. If end-conditions are conflicting, the condition closed curve
rules out other end conditions.
\end{minipg1} \\ \\
SYNOPSIS\\
	\>void s1334(\begin{minipg3}
		{\fov point}, {\fov numpt}, {\fov dim}, {\fov typept}, {\fov startcon}, {\fov endcon},
		{\fov open}, {\fov order},\\ {\fov startpar}, {\fov endpar}, {\fov curve}, {\fov pointpar},
		{\fov numptpar},{\fov stat})
		\end{minipg3}\\[0.3ex]
		\>\>	double	\> 	{\fov point}[\,];\\
		\>\>	int 	\>	{\fov numpt};\\
		\>\>	int 	\>	{\fov dim};\\
		\>\>	double 	\>	{\fov typept}[\,];\\
		\>\>	int 	\>	{\fov startcon};\\
		\>\>	int 	\>	{\fov endcon};\\
		\>\>	int 	\>	{\fov open};\\
		\>\>	int 	\>	{\fov order};\\
		\>\>	double 	\>	{\fov startpar};\\
		\>\>	double 	\>	*{\fov endpar};\\		
		\>\>	SISLCurve 	\>	**{\fov curve};\\
		\>\>	double 	\>	**{\fov pointpar};\\
		\>\>	int 	\>	*{\fov numptpar};\\
		\>\>	int 	\>	*{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
	\>\>	{\fov point}	\> - \>	\begin{minipg2}
				Array (length dim*numpt) containing the
				points/derivatives to be interpolated.
				\end{minipg2}\\[0.3ex]
	\>\>	{\fov numpt}	\> - \>	
				No. of points/derivatives in the
				point array.
				\\
	\>\>	{\fov dim}	\> - \>	\begin{minipg2}
				The dimension of the space in which
				the points lie.
				\end{minipg2}\\
	\>\>	{\fov typept}	\> - \>	\begin{minipg2}
				Array (length numpt) containing type
				indicator for points/derivatives:
				\end{minipg2} \\[0.3ex]
		\>\>\>\>\>	1 : Ordinary point.\\
		\>\>\>\>\>	3 : Derivative to next point.\\
		\>\>\>\>\>	4 : Derivative to prior point.\\
		\>\>\>\>\>	13 : Start-point of tangent to next point.\\
		\>\>\>\>\>	14 : End-point of tangent to prior point.\\
\newpagetabs
	\>\>	{\fov startcon}	\> - \>	\begin{minipg2}
				Additional condition at the start
				of the curve:
				\end{minipg2}\\
		\>\>\>\>\>	0 : 	No additional condition.\\
		\>\>\>\>\>	1 : 	Zero curvature at start.\\
	\>\>	{\fov endcon}	\> - \>	\begin{minipg2}
				Additional condition at the end
				of the curve:
				\end{minipg2}\\
		\>\>\>\>\>	0 : 	No additional condition.\\
		\>\>\>\>\>	1 : 	Zero curvature at end.\\
	\>\>	{\fov open}	\> - \>	Open or closed curve:\\
		\>\>\>\>\>	0 : 	Closed curve.\\
		\>\>\>\>\>	1 : 	Open curve.\\
	\>\>	{\fov order}	\> - \> \begin{minipg2}
				The order of the B-spline curve
				to be produced.
				\end{minipg2}\\
	\>\>	{\fov startpar}	\> - \>	\begin{minipg2}
				Parameter-value to be used at the
				start of the curve.
				\end{minipg2}\\
\\
	\>Output Arguments:\\
	\>\>	{\fov endpar}	\> - \>	\begin{minipg2}
				Parameter-value used at the end
				of the curve.
				\end{minipg2}\\
	\>\>	{\fov curve}	\> - \>	Pointer to output-curve\\
	\>\>	{\fov pointpar}	\> - \>	\begin{minipg2}
				Pointer to the parameter values of
				the interpolation conditions. Represented only once, although
				derivative conditions 
				will have the same 	
				parameter-value as the point.
				\end{minipg2} \\[0.3ex]
	\>\>	{\fov numptpar}	\> - \>	\begin{minipg2}
				No. of different parameter-values.
				\end{minipg2}\\
	\>\>	{\fov stat}	\> - \>	Status messages\\
		\>\>\>\>\>		$> 0$	: warning\\
		\>\>\>\>\>		$= 0$	: ok\\
		\>\>\>\>\>		$< 0$	: error\\
\newpagetabs
EXAMPLE OF USE\\
		\>	\{ \\
		\>\>	double	\> 	{\fov point}[30];\\
		\>\>	int 	\>	{\fov numpt} = 10;\\
		\>\>	int 	\>	{\fov dim} = 3;\\
		\>\>	double 	\>	{\fov typept}[10];\\
		\>\>	int 	\>	{\fov startcon};\\
		\>\>	int 	\>	{\fov endcon};\\
		\>\>	int 	\>	{\fov open};\\
		\>\>	int 	\>	{\fov order};\\
		\>\>	double 	\>	{\fov startpar};\\
		\>\>	double 	\>	{\fov endpar};\\		
		\>\>	SISLCurve 	\>	*{\fov curve};\\
		\>\>	double 	\>	*{\fov pointpar};\\
		\>\>	int 	\>	{\fov numptpar};\\
		\>\>	int 	\>	{\fov stat};\\
		\>\>	\ldots \\
	\>\>s1334(\begin{minipg4}
			{\fov point}, {\fov numpt}, {\fov dim}, {\fov typept},
			{\fov startcon}, {\fov endcon}, {\fov open}, {\fov order},\\ {\fov startpar},
			\&{\fov endpar}, \&{\fov curve}, \&{\fov pointpar}, \&{\fov numptpar}, \&{\fov stat});
			\end{minipg4}\\
		\>\>	\ldots \\
		\>	\} \\
\end{tabbing}
