\subsection{Degree reduction: B-spline curve as input.}
\funclabel{s1343}
\begin{minipg1}
  To approximate the input B-spline (i.e.\ NOT rational) curve by a
  cubic B-spline curve with error less than {\fov eps} in each of the
  {\fov kdim} components.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1343(\begin{minipg3}
        {\fov oldcurve}, {\fov eps}, {\fov startfix}, {\fov endfix}, {\fov epsco},
        {\fov itmax}, {\fov newcurve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov oldcurve};\\
                \>\>    double  \>      {\fov eps}[\,];\\
                \>\>    int     \>      {\fov startfix};\\
                \>\>    int     \>      {\fov endfix};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    int     \>      {\fov itmax};\\
                \>\>    SISLCurve       \>      **{\fov newcurve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov oldcurve}\> - \> Pointer to the old B-spline curve.\\
        \>\>    {\fov eps}      \> - \> \begin{minipg2}
                        Array (length kdim) giving the desired accuracy of
                                the spline-approximation in each component.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov startfix}\> - \>  \begin{minipg2}
                        The no. of derivatives that are not allowed to
                        change at the left end of the curve.
                        The $(0 - (startfix-1))$ derivatives
                        will be kept fixed. If startfix$<$0, this
                        routine will set it to 0. If startfix$>$order,
                        this routine will set it to order.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov endfix}   \> - \> \begin{minipg2}
                        The no. of derivatives that are not allowed to
                        change at the right end of the curve. The
                        $(0 - (endfix-1))$ derivatives will be kept fixed.
                        If endfix$<$0, this routine will set it to 0.
                        If endfix$>$order, this routine will set it to order.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov epsco}    \> - \> \begin{minipg2}
                        Two numbers differing by a relative amount
                        $<$epsco, will in some cases be considered equal. A
                        suitable value is just above the unit roundoff in the
                        machine.  The computations are not guaranteed to
                        have relative accuracy less than aepsco.
                        Not used anymore.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov itmax}    \> - \> \begin{minipg2}
                                Max. no. of iterations in the data-reduction routine.
                                \end{minipg2}\\[0.8ex]
        \>Output Arguments:\\
        \>\>    {\fov newcurve}\> - \> Pointer to the new B-spline curve.\\
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\newpagetabs
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov oldcurve};\\
                \>\>    double  \>      {\fov eps}[3];\\
                \>\>    int     \>      {\fov startfix};\\
                \>\>    int     \>      {\fov endfix};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    int     \>      {\fov itmax};\\
                \>\>    SISLCurve       \>      *{\fov newcurve};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1343(\begin{minipg4}
        {\fov oldcurve}, {\fov eps}, {\fov startfix}, {\fov endfix}, {\fov epsco},
        {\fov itmax}, \&{\fov newcurve}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \} \\
\end{tabbing}
