\subsection{Intersection between a curve and a 2D circle or a sphere.}
\funclabel{s1371}
\begin{minipg1}
  Find all the intersections between a curve and a sphere
  (if curve dimension and $dim=3$), or a curve and a circle
  (if curve dimension and $dim=2$).
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1371(\begin{minipg3}
        {\fov curve}, {\fov centre}, {\fov radius}, {\fov dim}, {\fov epsco}, {\fov epsge}, {\fov numintpt}, {\fov intpar},\\
                        {\fov numintcu}, {\fov intcurve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov centre}[\,];\\
                \>\>    double  \>      {\fov radius};\\
                \>\>    int     \>      {\fov dim};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov numintpt};\\
                \>\>    double  \>      **{\fov intpar};\\
                \>\>    int     \>      *{\fov numintcu};\\
                \>\>    SISLIntcurve \> ***{\fov intcurve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve}    \> - \> Pointer to the curve.\\
        \>\>    {\fov centre}   \> - \> Centre of the circle/sphere.\\
        \>\>    {\fov radius}   \> - \> Radius of circle or sphere.\\
        \>\>    {\fov dim}      \> - \> \begin{minipg2}
                                Dimension of the space in which the
                                curve and the circle/sphere lies, {\fov dim}
                                should be equal to two or three.
                                \end{minipg2}\\[0.3ex]
        \>\>    {\fov epsco}    \> - \> Computational resolution (not used).\\
        \>\>    {\fov epsge}    \> - \> Geometry resolution.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov numintpt}\> - \>  Number of single intersection points.\\
        \>\>    {\fov intpar}   \> - \> \begin{minipg2}
                        Array containing the parameter values of the
                        single intersection points in the parameter
                        interval of the curve. The points lie in sequence.
                        Intersection curves are stored in intcurve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numintcu}\> - \>Number of intersection curves.\\
        \>\>    {\fov intcurve}\> - \>  \begin{minipg2}
                        Array of pointers to SISLIntcurve objects
                        containing descriptions of the intersection
                        curves. The curves are only described by start
                        points and end points in
                        the parameter interval of the curve. The curve
                        pointers point to nothing.
                                \end{minipg2}\\[0.8ex]
\newpagetabs
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    double  \>      {\fov centre}[3];\\
                \>\>    double  \>      {\fov radius};\\
                \>\>    int     \>      {\fov dim} = 3;\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      {\fov numintpt};\\
                \>\>    double  \>      *{\fov intpar};\\
                \>\>    int     \>      {\fov numintcu};\\
                \>\>    SISLIntcurve \> **{\fov intcurve};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1371(\begin{minipg4}
        {\fov curve}, {\fov centre}, {\fov radius}, {\fov dim}, {\fov epsco}, {\fov epsge}, \&{\fov numintpt},
                \&{\fov intpar}, \&{\fov numintcu}, \&{\fov intcurve}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
