\subsection{Compute volume between a B-spline surface and a point.}
\funclabel{s1441}
\begin{minipg1}
Compute the volume of the object surrounded by the input surface and the 
surface defined by the reference point and the boundary of the input surface. The 
volume might have a negative value dependent on the "direction" of the surface 
relative to the reference point. When used on a closed surface, the routine 
gives as output the volume of the object surrounded by the surface. The 
difference between the volume calculated and the real volume will be less than 
(epssurf/the volume calculated).
\end{minipg1} \\ \\
SYNOPSIS\\
	\>void s1441	(\begin{minipg3}
				{\fov surf}, {\fov point}, {\fov dim}, {\fov epssurf}, {\fov epsge}, {\fov volume}, {\fov stat})
		\end{minipg3}\\[0.3ex]

		\>\>	SISLSurf	\> 	*{\fov surf};\\
		\>\>	double	\>	{\fov point}[\,];\\
		\>\>	int	\>	{\fov dim};\\
		\>\>	double 	\>	{\fov epssurf};\\
		\>\>	double	\>	{\fov epsge};\\
		\>\>	double	\>	*{\fov volume};\\
		\>\>	int 	\>	*{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
	\>\>	{\fov surf}\> - \>	\begin{minipg2}
				Pointer to the surface.
				\end{minipg2}\\
	\>\>	{\fov point}\> - \>	\begin{minipg2}
				Reference point in the volume computation.
				\end{minipg2}\\
	\>\>	{\fov dim}\> - \>	\begin{minipg2}
				Dimension of the space in which the point and surface lie.
				\end{minipg2}\\
	\>\>	{\fov epssurf}\> - \>	\begin{minipg2}
				Relative resolution used on surfaces.
				\end{minipg2} \\
	\>\>	{\fov epsge}\> - \> \begin{minipg2}
				Geometry resolution.
				\end{minipg2}\\
\\
	\>Output Arguments:\\
	\>\>	{\fov volume}\> - \>	\begin{minipg2}
				The volume calculated
				\end{minipg2}\\
	\>\>	{\fov stat}	\> - \>	Status messages\\
		\>\>\>\>\>		$> 0$	: warning\\
		\>\>\>\>\>		$= 0$	: ok\\
		\>\>\>\>\>		$< 0$	: error\\
\\
EXAMPLE OF USE\\
		\>	\{ \\
		\>\>	SISLSurf	\> 	*{\fov surf};\\
		\>\>	double	\>	{\fov point[3]};\\
		\>\>	int	\>	{\fov dim = 3};\\
		\>\>	double 	\>	{\fov epssurf};\\
		\>\>	double	\>	{\fov epsge};\\
		\>\>	double	\>	{\fov volume};\\
		\>\>	int 	\>	{\fov stat};\\
		\>\>	\ldots \\
	\>\>s1441	(\begin{minipg4}
		{\fov surf}, {\fov point}, {\fov dim}, {\fov epssurf}, {\fov epsge}, \&{\fov volume}, \&{\fov stat});
			\end{minipg4}\\
		\>\>	\ldots \\
		\>	\}
\end{tabbing}
