\subsection{Compute volume, weight point and moment of inertia of an object defined by a B-spline 
patch and a point.}
\funclabel{s1443}
\begin{minipg1}
Compute the volume and the weight point of the object surrounded (by the 
input 
surface and the surface defined by the reference point) and boundary of the input surface, by using recursive subdivision. The 
rotational momentum relative to a given axis is also calculated. The 
difference between the volume computed and the real volume of the object 
is 
less than (epssurf/volume computed).
\end{minipg1} \\ \\
SYNOPSIS\\
	\>void s1443(\begin{minipg3}
			{\fov surf}, {\fov refpoint}, {\fov axpoint}, {\fov dir}, {\fov dim}, {\fov epssurf}, {\fov epsge}, {\fov weight}, 	
			{\fov volume}, {\fov moment}, {\fov stat}))
		\end{minipg3}\\[0.3ex]

		\>\>	SISLSurf	\> 	*{\fov surf};\\
		\>\>	double	\>	{\fov refpoint}[\,];\\
		\>\>	double	\>	{\fov axpoint}[\,];\\
		\>\>	double 	\>	{\fov dir}[\,];\\
		\>\>	int 	\>	{\fov dim};\\
		\>\>	double	\>	{\fov epssurf};\\
		\>\>	double 	\>	{\fov epsge};\\
		\>\>	double 	\>	{\fov weight}[\,];\\
		\>\>	double 	\>	*{\fov volume};\\
		\>\>	double	\>	*{\fov moment};\\
		\>\>	int 	\>	*{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
	\>\>	{\fov surf}\> - \>	\begin{minipg2}
				Pointer to the surface.
				\end{minipg2}\\
	\>\>	{\fov refpoint}\> - \>	\begin{minipg2}
				Reference point in volume computation.
				\end{minipg2}\\
	\>\>	{\fov axpoint}\> - \>		\begin{minipg2}
				Point on the rotational axis.
				\end{minipg2}\\
	\>\>	{\fov dir}\> - \>	\begin{minipg2}
				Direction of the rotational axis
				\end{minipg2} \\
	\>\>	{\fov dim}\> - \> 	\begin{minipg2}
				Dimension of the space in which point, axpoint and dir 
				lie.
				\end{minipg2}\\[0.8ex]
	\>\>	{\fov epssurf}\> - \>	\begin{minipg2}
				Relative resolution used on surfaces.
				\end{minipg2}\\
	\>\>	{\fov epsge}\> - \>	\begin{minipg2}
				Geometry resolutions.
				\end{minipg2}\\
\\
	\>Output Arguments:\\
	\>\>	{\fov weight}\> - \>	\begin{minipg2}
				Weight point of object.
				\end{minipg2}\\
	\>\>	{\fov volume}\> - \>		\begin{minipg2}
				The volume calculated.
				\end{minipg2}\\
	\>\>	{\fov moment}\> - \>	\begin{minipg2}
				Rotational weight moment.
				\end{minipg2}\\
	\>\>	{\fov stat}	\> - \>	Status messages\\
		\>\>\>\>\>		$> 0$	: warning\\
		\>\>\>\>\>		$= 0$	: ok\\
		\>\>\>\>\>		$< 0$	: error\\
\\
EXAMPLE OF USE\\
		\>	\{ \\
		\>\>	SISLSurf	\> 	*{\fov surf};\\
		\>\>	double	\>	{\fov refpoint[3]};\\
		\>\>	double	\>	{\fov axpoint[3]};\\
		\>\>	double 	\>	{\fov dir[3]};\\
		\>\>	int 	\>	{\fov dim = 3};\\
		\>\>	double	\>	{\fov epssurf};\\
		\>\>	double 	\>	{\fov epsge};\\
		\>\>	double 	\>	{\fov weight[3]};\\
		\>\>	double 	\>	{\fov volume};\\
		\>\>	double	\>	{\fov moment};\\
		\>\>	int 	\>	stat;\\
		\>\>	\ldots \\
	\>\>s1443(\begin{minipg4}
		{\fov surf}, {\fov refpoint}, {\fov axpoint}, {\fov dir}, {\fov dim}, {\fov epssurf}, {\fov epsge}, {\fov weight},\linebreak
		\&{\fov volume},\&{\fov moment}, \&{\fov stat});
			\end{minipg4}\\
		\>\>	\ldots \\
		\>	\}
\end{tabbing}
