\subsection{Offset surface.}
\funclabel{s1452}
\begin{minipg1}
To make a B-spline surface approximating an offset surface using a given distance from the input surface.
\end{minipg1} \\ \\
SYNOPSIS\\
	\>void s1452(\begin{minipg3}
				{\fov surf}, {\fov epsge}, {\fov offdist}, {\fov newsurf}, {\fov stat})
		\end{minipg3}\\[0.3ex]

		\>\>	SISLSurf	\> 	*{\fov surf};\\
		\>\>	double	\>	{\fov epsge};\\
		\>\>	double	\>	{\fov offdist};\\
		\>\>	SISLSurf	\>	**{\fov newsurf};\\
		\>\>	int 	\>	*{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
	\>\>	{\fov surf}\> - \>	\begin{minipg2}
			Pointer to the surface from which the offset surface is to be made.
				\end{minipg2}\\[0.8ex]
	\>\>	{\fov epsge}\> - \>	\begin{minipg2}
			Accepted deviation between the true offset surface and the approximated 
			offset surface. If a small tolerance is 
			given, the execution time will be long.
				\end{minipg2}\\[0.3ex]
	\>\>	{\fov offdist}\> - \>	\begin{minipg2}
				The offset distance. If offdist is 
				positive the offset will be along the 
				positive direction of the normal vector, 
				else along the negative 
				direction.	
				\end{minipg2}\\[0.3ex]
	\>Output Arguments:\\
	\>\>	{\fov newsurf}\> - \>	\begin{minipg2}
				The produced offset surface.	
				\end{minipg2}\\
	\>\>	{\fov stat}	\> - \>	Status messages\\
		\>\>\>\>\>		$> 0$	: warning\\
		\>\>\>\>\>		$= 0$	: ok\\
		\>\>\>\>\>		$< 0$	: error\\
EXAMPLE OF USE\\
		\>	\{ \\
		\>\>	SISLSurf	\> 	*{\fov surf};\\
		\>\>	double	\>	{\fov epsge};\\
		\>\>	double	\>	{\fov offdist};\\
		\>\>	SISLSurf	\>	*{\fov newsurf};\\
		\>\>	int 	\>	{\fov stat};\\
		\>\>	\ldots \\
	\>\>s1452(\begin{minipg4}
		{\fov surf}, {\fov epsge}, {\fov offdist},\&{\fov newsurf}, \&{\fov stat});
			\end{minipg4}\\
		\>\>	\ldots \\
		\>	\}
\end{tabbing}
