\subsection{Newton iteration on the intersection between a 3D NURBS surface and a line.}
\funclabel{s1518}
\begin{minipg1}
Newton iteration on the intersection between
               a 3D NURBS surface and a line.
               If a good initial guess is given, the intersection will
               be found quickly. However if a bad initial guess is given,
               the iteration might not converge.
               We only search in the rectangular subdomain specified
               by "start" and "end". This can be the whole domain if desired.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>     void s1518(\begin{minipg3}
            {\fov surf},  {\fov point},  {\fov dir},  {\fov epsge},  {\fov start},  {\fov end},  {\fov parin},  {\fov parout},  {\fov stat})
                \end{minipg3}\\
                \>\>    SISLSurf    \>  *{\fov surf};\\
                \>\>    double \> point[\,];\\
                \>\>    double \> dir[\,];\\
                \>\>    double \> epsge;\\
                \>\>    double \> start[\,];\\
                \>\>    double \> end[\,];\\
                \>\>    double \> parin[\,];\\
                \>\>    double \> parout[\,];\\
                \>\>    int    \>  *{\fov stat};\\
\\
ARGUMENTS\\
	\>Input Arguments:\\
        \>\>    {\fov surf}\> - \>  \begin{minipg2}
                     The NURBS surface.
                               \end{minipg2}\\
        \>\>    {\fov point}\> - \>  \begin{minipg2}
                     A point on the line.
                               \end{minipg2}\\
        \>\>    {\fov dir}\> - \>  \begin{minipg2}
                     The vector direction of the line
                        (not necessarily normalized).
                               \end{minipg2}\\
        \>\>    {\fov epsge}\> - \>  \begin{minipg2}
                     Geometric resolution.
                               \end{minipg2}\\
        \>\>    {\fov start}\> - \>  \begin{minipg2}
                     Lower limits of search rectangle (umin, vmin).
                               \end{minipg2}\\
        \>\>    {\fov end}\> - \>  \begin{minipg2}
                     Upper limits of search rectangle (umax, vmax).
                               \end{minipg2}\\
        \>\>    {\fov parin}\> - \>  \begin{minipg2}
                     Initial guess (u0,v0) for parameter point of
                        intersection (which should be inside the
                        search rectangle).
                               \end{minipg2}\\
\\
	\>Output Arguments:\\
        \>\>    {\fov parout}\> - \>  \begin{minipg2}
                     Parameter point (u,v) of intersection.
                               \end{minipg2}\\
        \>\>    {\fov jstat}\> - \>  \begin{minipg2}
                     status messages  
                                = 1   : Intersection found.
                                < 0   : error.
                               \end{minipg2}\\
\\
EXAMPLE OF USE\\
		\>      \{ \\

                \>\>    SISLSurf    \>  *{\fov surf};\\
                \>\>    double \> point[\,];\\
                \>\>    double \> dir[\,];\\
                \>\>    double \> epsge;\\
                \>\>    double \> start[\,];\\
                \>\>    double \> end[\,];\\
                \>\>    double \> parin[\,];\\
                \>\>    double \> parout[\,];\\
                \>\>    int    \>  *{\fov stat};\\                \>\>    \ldots \\
        \>    \>s1518(\begin{minipg4}
            {\fov surf},  {\fov point},  {\fov dir},  {\fov epsge},  {\fov start},  {\fov end},  {\fov parin},  {\fov parout},  {\fov stat});
                \end{minipg4}\\
                \>\>    \ldots \\
		\>      \}
\end{tabbing}
