\subsection{Pick the next Bezier surface from a surface.}
\funclabel{s1733}
\begin{minipg1}
  To pick the next Bezier surface from a surface. This function
  requires a surface represented as the result of s1731(). See page
  \pageref{s1731}.
  This routine does not check that the surface is correct.
  If the input surface is rational, the generated Bezier surfaces will be
  rational too (i.e.\ there will be rational weights in the
  representation of the Bezier surfaces).
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1733(\begin{minipg3}
                {\fov surf}, {\fov number1}, {\fov number2}, {\fov startpar1}, {\fov endpar1}, {\fov startpar2},
                 \linebreak  {\fov endpar2}, {\fov coef}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLSurf        \>      *{\fov surf};\\
                \>\>    int     \>      {\fov number1};\\
                \>\>    int     \>      {\fov number2};\\
                \>\>    double  \>      *{\fov startpar1};\\
                \>\>    double  \>      *{\fov endpar1};\\
                \>\>    double  \>      *{\fov startpar2};\\
                \>\>    double  \>      *{\fov endpar2};\\
                \>\>    double  \>      {\fov coef}[\,];\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov surf}\> - \>      \begin{minipg2}
                                The surface to convert.
                                \end{minipg2}\\
        \>\>    {\fov number1}\> - \>
        \begin{minipg2}
          The number of the Bezier patch to pick in the horizontal
          direction, where $0\leq number1<in1/ik1$ of the surface.
        \end{minipg2}\\[0.8ex]
        \>\>    {\fov number2}\> - \>
        \begin{minipg2}
          The number of the Bezier patch to pick in the vertical
          direction, , where $0\leq number2<in2/ik2$ of the surface.
        \end{minipg2}\\[0.8ex]
\\
        \>Output Arguments:\\
        \>\>    {\fov startpar1}        \> - \> \begin{minipg2}
                                The start parameter value of the Bezier
                                patch in the horizontal direction.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov endpar1}  \> - \> \begin{minipg2}
                                The end parameter value of the Bezier
                                patch in the horizontal direction.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov startpar2}        \> - \> \begin{minipg2}
                                The start parameter value of the Bezier patch                           in the vertical direction.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov endpar2}  \> - \> \begin{minipg2}
                                The end parameter value of the Bezier patch                             in the vertical direction.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov coef}     \> - \>
        \begin{minipg2}
          The vertices of the Bezier patch.
          Space must be allocated with a size of $(idim+1)\times ik1\times ik2$
          as given by the surface (this is done for reasons of efficiency).
        \end{minipg2}\\
\newpagetabs
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error
\\
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLSurf        \>      *{\fov surf};\\
                \>\>    int     \>      {\fov number1};\\
                \>\>    int     \>      {\fov number2};\\
                \>\>    double  \>      {\fov startpar1};\\
                \>\>    double  \>      {\fov endpar1};\\
                \>\>    double  \>      {\fov startpar2};\\
                \>\>    double  \>      {\fov endpar2};\\
                \>\>    double  \>      {\fov coef}[48];\\
                \>\>    int     \>      stat;\\
                \>\>    \ldots \\
        \>\>s1733(\begin{minipg4}
                {\fov surf}, {\fov number1}, {\fov number2}, \&{\fov startpar1}, \&{\fov endpar1},
                        \&{\fov startpar2}, \&{\fov endpar2}, {\fov coef}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
