\subsection{Pick out the next Bezier curve from a curve.}
\funclabel{s1732}
\begin{minipg1}
  To pick out the next Bezier curve from a curve. This function requires a
  curve represented as the curve that is output from s1730().
  If the input curve is rational, the generated Bezier curves will be
  rational too (i.e.\ there will be rational weights in the
  representation of the Bezier curves).
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1732(\begin{minipg3}
        {\fov curve}, {\fov number}, {\fov startpar}, {\fov endpar}, {\fov coef}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    int     \>      {\fov number};\\
                \>\>    double  \>      *{\fov startpar};\\
                \>\>    double  \>      *{\fov endpar};\\
                \>\>    double  \>      {\fov coef}[\,];\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve}    \> - \> curve to pick from.\\
        \>\>    {\fov number}   \> - \>\begin{minipg2}
                                The number of the Bezier curve that is
                                to be picked, where $0\leq number<in/ik$
                                (i.e.\ the number of vertices in the
                                curve divided by the order of the curve).
                                \end{minipg2}\\[0.8ex]
\\
        \>Output Arguments:\\
        \>\>    {\fov startpar}\> - \>\begin{minipg2}
                                The start parameter value of the Bezier curve.
                                \end{minipg2}\\
        \>\>    {\fov endpar} \> - \>\begin{minipg2}
                                The end parameter value of the Bezier curve.
                                \end{minipg2}\\
        \>\>    {\fov coef}     \> - \>\begin{minipg2}
                                The vertices of the Bezier curve.
                                Space of size $(idim+1)\times ik$ (i.e.\
                                spatial dimension of curve $+1$ times the
                                order of the curve) must be allocated
                                outside the function.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\newpagetabs
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov curve};\\
                \>\>    int     \>      {\fov number};\\
                \>\>    double  \>      {\fov startpar};\\
                \>\>    double  \>      {\fov endpar};\\
                \>\>    double  \>      {\fov coef}[12];\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1732(\begin{minipg4}
                {\fov curve}, {\fov number}, \&{\fov startpar}, \&{\fov endpar}, {\fov coef}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
