\subsection{\sloppy Intersection between two curves.}
\funclabel{s1857}
\begin{minipg1}
  Find all the intersections between two curves.
\end{minipg1} \\ \\
SYNOPSIS\\
        \>void s1857(\begin{minipg3}
        {\fov curve1}, {\fov curve2}, {\fov epsco}, {\fov epsge}, {\fov numintpt},
        {\fov intpar1}, {\fov intpar2}, {\fov \\numintcu}, {\fov intcurve}, {\fov stat})
                \end{minipg3}\\[0.3ex]
                \>\>    SISLCurve       \>      *{\fov curve1};\\
                \>\>    SISLCurve       \>      *{\fov curve2};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      *{\fov numintpt};\\
                \>\>    double  \>      **{\fov intpar1};\\
                \>\>    double  \>      **{\fov intpar2};\\
                \>\>    int     \>      *{\fov numintcu};\\
                \>\>    SISLIntcurve \> ***{\fov intcurve};\\
                \>\>    int     \>      *{\fov stat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov curve1}   \> - \> Pointer to the first curve.\\
        \>\>    {\fov curve2}   \> - \> Pointer to the second curve.\\
        \>\>    {\fov epsco}    \> - \> Computational resolution (not used).\\
        \>\>    {\fov epsge}    \> - \> Geometry resolution.\\
\\
        \>Output Arguments:\\
        \>\>    {\fov numintpt}\> - \>  Number of single intersection points.\\
        \>\>    {\fov intpar1}  \> - \> \begin{minipg2}
                        Array containing the parameter values of the
                        single intersection points in the parameter
                        interval of the first curve.
                        Intersection curves are stored in intcurve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov intpar2}  \> - \> \begin{minipg2}
                        Array containing the parameter values of the
                        single intersection points in the parameter
                        interval of the second curve.
                        Intersection curves are stored in intcurve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov numintcu}\> - \>Number of intersection curves.\\
        \>\>    {\fov intcurve}\> - \>  \begin{minipg2}
                        Array of pointers to the SISLIntcurve objects
                        containing descriptions of the intersection
                        curves. The curves are only described by start
                        points and end points in the parameter interval
                        of the curve. The curve pointers point
                        to nothing.
                        If the curves given as input are
                        degenerate, an intersection point can be returned as
                        an intersection curve.
                                \end{minipg2}\\[0.8ex]
        \>\>    {\fov stat}     \> - \> Status messages\\
                \>\>\>\>\>              $> 0$   : warning\\
                \>\>\>\>\>              $= 0$   : ok\\
                \>\>\>\>\>              $< 0$   : error\\
\\ %\newpagetabs
EXAMPLE OF USE\\
                \>      \{ \\
                \>\>    SISLCurve       \>      *{\fov curve1};\\
                \>\>    SISLCurve       \>      *{\fov curve2};\\
                \>\>    double  \>      {\fov epsco};\\
                \>\>    double  \>      {\fov epsge};\\
                \>\>    int     \>      {\fov numintpt};\\
                \>\>    double  \>      *{\fov intpar1};\\
                \>\>    double  \>      *{\fov intpar2};\\
                \>\>    int     \>      {\fov numintcu};\\
                \>\>    SISLIntcurve \> **{\fov intcurve};\\
                \>\>    int     \>      {\fov stat};\\
                \>\>    \ldots \\
        \>\>s1857(\begin{minipg4}
                {\fov curve1}, {\fov curve2}, {\fov epsco}, {\fov epsge}, \&{\fov numintpt},
                \&{\fov intpar1}, \&{\fov intpar2}, \&{\fov numintcu}, \&{\fov intcurve}, \&{\fov stat});
                        \end{minipg4}\\
                \>\>    \ldots \\
                \>      \}
\end{tabbing}
