\subsection{Find the closest point between a surface and a point.
Simple version.}
\funclabel{s1958}
\begin{minipg1}
  Find the closest point between a surface and a point.
  The method is fast and should work well in clear cut cases, but there is
  no guarantee it will find the right solution. As long as it doesn't
  fail, it will find exactly one point.  In other cases, use s1954() on
  page~\pageref{s1954}.
\end{minipg1}\\ \\
SYNOPSIS\\
        \>void s1958(\begin{minipg3}
          {\fov psurf}, {\fov epoint}, {\fov idim}, {\fov aepsco}, {\fov aepsge}, {\fov gpar}, {\fov dist}, {\fov jstat})
        \end{minipg3}\\[0.3ex]
        \>\>    SISLSurf \> *{\fov psurf};\\
        \>\>    double   \> {\fov epoint}[\,];\\
        \>\>    int      \> {\fov idim};\\
        \>\>    double   \> {\fov aepsco};\\
        \>\>    double   \> {\fov aepsge};\\
        \>\>    double   \> {\fov gpar}[\,];\\
        \>\>    double   \> *{\fov dist};\\
        \>\>    int    \>  *{\fov jstat};\\
\\
ARGUMENTS\\
        \>Input Arguments:\\
        \>\>    {\fov psurf}\> - \>  \begin{minipg2}
                     Pointer to the surface in the closest point problem.
                               \end{minipg2}\\
        \>\>    {\fov epoint}\> - \>  \begin{minipg2}
                     The point in the closest point problem.
                               \end{minipg2}\\
        \>\>    {\fov idim}\> - \>  \begin{minipg2}
                     Dimension of the space in which epoint lies.
                               \end{minipg2}\\
        \>\>    {\fov aepsco}\> - \>  \begin{minipg2}
                     Computational resolution (not used).
                               \end{minipg2}\\
        \>\>    {\fov aepsge}\> - \>  \begin{minipg2}
                     Geometry resolution.
                               \end{minipg2}\\
\\
        \>Output Arguments:\\
        \>\>    {\fov gpar}\> - \>  \begin{minipg2}
                     2D array containing the parameter values of the
                       closest point in the parameter space
                       of the surface.
                               \end{minipg2}\\
        \>\>    {\fov dist}\> - \>  \begin{minipg2}
                     The closest distance between point and the surface.
                               \end{minipg2}\\
        \>\>    {\fov jstat}     \> - \> Status messages\\
                \>\>\>\>              $> 2$ \> : Warning.\\
                \>\>\>\>              $= 2$ \> : Solution at a corner.\\
                \>\>\>\>              $= 1$ \> : Solution at an edge.\\
                \>\>\>\>              $= 0$ \> : Solution in interior.\\
                \>\>\>\>              $< 0$ \> : Error.\\
\newpagetabs
EXAMPLE OF USE\\
        \>      \{ \\
        \>\>    SISLSurf  \>  *{\fov psurf};\\
        \>\>    double    \>  {\fov epoint}[3];\\
        \>\>    int       \>  {\fov idim} = 3;\\
        \>\>    double    \>  {\fov aepsco};\\
        \>\>    double    \>  {\fov aepsge};\\
        \>\>    double    \>  {\fov gpar}[2];\\
        \>\>    double    \>  {\fov dist} = 0;\\
        \>\>    int       \>  {\fov jstat} = 0;\\
        \>\>    \ldots \\
        \>\>s1958(\begin{minipg4}
          {\fov psurf}, {\fov epoint}, {\fov idim}, {\fov aepsco}, {\fov aepsge}, {\fov gpar}, \&{\fov dist}, \&{\fov jstat});
        \end{minipg4}\\
        \>\>    \ldots \\
        \>      \}
\end{tabbing}
