\chapter{Curve Definition}
\label{curvedefinition}

This chapter describes all functions in the Curve Definition module.
\section{Interpolation}
In this section we treat different kinds of interpolation of
points or points and derivatives (Hermite). In addition to the general
functions there are functions to find fillet curves
(a curve between two other curves),
and blending curves (a curve between the end points of two other curves).
\input{func/s1602}
\pgsbreak
\input{func/s1356}
\pgsbreak
\input{func/s1357}
\pgsbreak
\input{func/s1380}
\pgsbreak
\input{func/s1379}
\pgsbreak
\input{func/s1607}
\pgsbreak
\input{func/s1608}
\pgsbreak
\input{func/s1609}
\pgsbreak
\input{func/s1014}
\pgsbreak
\input{func/s1015}
\pgsbreak
\input{func/s1016}
\pgsbreak
\input{func/s1606}
\pgsbreak
\section{Approximation}
Two kinds of curves are treated in this section.
The first is approximations of special shapes like
circles and conic segments.
The second is approximation of a point set, or offsets to curves.

Except for the point set approximation function, all functions
require a tolerance for the approximation.
Note that there is a close relationship
between the size of the tolerance and the amount of data
for the curve.
\input{func/s1303}
\pgsbreak
\input{func/s1611}
\pgsbreak
\input{func/s1630}
\pgsbreak
\input{func/s1360}
\pgsbreak
\input{func/s1613}
\pgsbreak
\input{func/s1600}
\pgsbreak
\section{Conversion}
\input{func/s1389}
\pgsbreak
\input{func/s1730}
\pgsbreak
\input{func/s1732}
\pgsbreak
\input{func/s1750}
\pgsbreak
\input{func/s1720}
\pgsbreak
\input{func/s1522}
\pgsbreak
\input{func/s1011}
\pgsbreak
\input{func/s1012}
